\section{Give Me a Hand}\label{test:give-me-a-hand}

\subsection*{Description}
The robot assists a human in organizing new items by receiving them and placing them in specified locations using natural interaction.

\textbf{Main goal:}
New items have arrived at the house. The operator takes each item from a container, hands it to the robot, and instructs the robot to place it at a designated location within the room.

\subsection*{Focus}
\emph{Object perception}, \emph{Human perception}, \emph{Verbal interaction}, and \emph{Human-Robot Interaction}.

\subsection*{Setup}
\begin{itemize}[nosep]	
	\item \textbf{Locations:} 
	\begin{itemize}
		\item This test takes place inside the Arena in a single room.
	\end{itemize}	 
	\item \textbf{People:} 
	\begin{itemize}
		\item The operator remains in a fixed location during the test.
		\item Other people (e.g., referee, assistant) may be present in the room.
	\end{itemize}
	\item \textbf{Objects:}
		\begin{itemize}
			\item A container (box or bag) containing five random known objects (see \ref{rule:scenario_objects}).
			\item Several visually similar delivery locations (e.g., identical bowls, plates, or bins) placed within the room to create ambiguity.
		\end{itemize}
\end{itemize}

\subsection*{Procedure}
\begin{enumerate}[nosep]
	\item The robot starts outside the arena and navigates to the designated room once the door is opened.
	\item The robot approaches the operator, who remains stationary throughout the test.
	\item The operator picks up an object from the container and hands it to the robot.
	\item The operator issues a verbal instruction for where to place the item. Instructions may include gestures and references to landmarks.
	\item The robot delivers the item to the specified location, then returns to the operator for the next object.
	\item Steps 3--5 repeat until all five items are delivered.
\end{enumerate}

\subsection*{Additional rules and remarks}
\begin{enumerate}[nosep]
	\item \textbf{Handover:}
	\begin{itemize}[nosep]
		\item The robot must clearly signal its readiness to receive the item (e.g., by holding its manipulator still, using lights, audio cues, or verbal prompts).
		\item The manipulator must be positioned within 10--20 cm of the operator's hand, without initiating contact.
		\item The operator must complete the handover; the robot must not reach, grasp, or initiate movement toward the human.
		\item Explicit verbal guidance from the operator (e.g., \textit{"Place the item in my gripper, I'll close it in 3…2…1"}) is considered \textit{Deus ex Machina} and will result in penalties.
		\item The robot may, however, issue natural cues such as: \textit{"I detect the object in my hand. I will close my gripper in 3 seconds, please be careful."}.
	\end{itemize}

	\item \textbf{Delivery:}
	\begin{itemize}[nosep]
		\item Delivery instructions may combine verbal commands with gestures (e.g., \textit{"Put this on that plate, next to the flower vase"} while pointing).
		\item The robot is expected to use natural interaction to confirm ambiguous instructions.
		\item Since the target locations are intentionally ambiguous, the robot can request clarification from the operator before proceeding. This should be done through natural interaction, such as verbal questions or multimodal cues (e.g., pointing, asking \textit{"Which one?”}).
		\item Full points are awarded only if the object is placed in the correct container or within a few centimeters of the intended target.
		\item Human-robot interaction must be natural: robots must first capture the operator's attention (e.g., by gesture, light, or audio) before initiating clarification — especially if the operator is distracted or not directly facing the robot.
		\item Interactions where the robot talks without attention capture (e.g., asking questions while the operator is busy elsewhere) are discouraged and may affect scoring.
	\end{itemize}
\end{enumerate}

\subsection*{Instructions:}
\subsubsection*{Referee instructions}

The referee needs to:
\begin{itemize}[nosep]
	\item Randomly select five known scenario objects and corresponding delivery locations.
	\item Assign the operator's location in the room.
\end{itemize}

\subsubsection*{OC Instructions}
At least two hours before the test:
\begin{itemize}[nosep]
	\item Announce the room for the test.
	\item Arrange target containers and placement items (such as similar bowls, dishes, or bins) around the room to create ambiguity in delivery instructions.
\end{itemize}

\subsection*{Score sheet}
\input{scoresheets/GiveMeAHand.tex}
