\section{Stickler for the Rules}
\label{test:stickler-for-the-rules}

\subsection*{Description}
The robot needs to make sure the house rules are followed.

\textbf{Main goal:}
Identify party guests breaking the house rules, politely clarify to the guest what to do and confirm that the guest is following the rule.

\textbf{Optional goal:}
Politely clarify to the guest what rule is being broken.


\subsection*{Focus}
This task focuses on
\textit{Object perception},
\textit{Human perception},
\textit{Action recognition} and
\textit{Verbal interaction}.

\subsection*{Setup}
\begin{itemize}[nosep]	
	\item \textbf{Locations:} 
	\begin{itemize}
		\item This task takes place inside the \Arena{}.
		\item The robot starts at a predefined location in the living room.
		\item There are a forbidden room in the house.
	\end{itemize}	 
	\item \textbf{People:} 
	\begin{itemize}
		\item There are at least five party guests inside the \Arena{}.
		\item Four of the guests are breaking rules.
		\item Guests may not follow the robot's instructions.
	\end{itemize}
	\item \textbf{Furniture:} All furniture are in their predefined locations.
	\item \textbf{Objects:} All objects are in their predefined locations.
\end{itemize}

\subsection*{Procedure}
	\begin{enumerate}[nosep]
		\item The referee requests the team to move the robot to the start location.
		\item The referee gives the start signal and starts the timer.
		\item The team leaves the area after the start signal.		
		\item A TC member follows the robot ready to press the emergency stop button.
		\item The robot Identify party guests breaking the house rules.
		\item The robot politely clarify to the guest what to do. 
		\item The robot confirm that the guest is following the rule.	
		\item \textbf{Optionally} and Politely, the robot clarify to the guest what rule is being broken.
	\end{enumerate}


\subsection*{Additional rules and remarks}
\begin{itemize}[nosep]
	\item \textbf{House Rules:}
	\begin{enumerate}[nosep]
		\item \textit{No shoes inside the house.}\\
		\textbf{Policy:} All guests have to take off their shoes at the entrance.\\
		\textbf{Action:} Take the guests to the entrance and verify they take off their shoes.
	
		\item \textit{Forbidden room}\\
		\textbf{Policy:} No guests are allowed in the \emph{Forbidden Room}. \\
		\textbf{Action:} Take the offenders to the other party guests and verify they don't enter back.
	
		\item \textit{No littering}\\
		\textbf{Policy:} Guests are not allowed to leave garbage on the floor.\\
		\textbf{Action:} Make the (closest) offender pick up the garbage and throw it into the bin.
	
		\item \textit{Compulsory hydration}\\
		\textbf{Policy:} All guests must have a drink in hand at all times.\\
		\textbf{Action:} Take the guests to the kitchen/bar and make sure they grab a drink.
	\end{enumerate}
	\item \textbf{Talking to no one:} If the robot is talking to the empty arena or a wall, no additional penalty is applied. 
	\item \textbf{Number of Rulebreakers:} Each rule is being broken 0-2 times. There are at least 3 different kind of rules being broken in the arena.
	\item \textbf{Confirm the Following of a Rule:} When given instructions the guests might not immediately follow them. The robot needs to re-check and confirm that the rule is not being broken anymore. Once the robot has confirmed this it can be assumed that the person is no longer breaking rules.
\end{itemize}

\subsection*{Instructions:}
\subsubsection*{Referee instructions}

\begin{itemize}
	\item Instruct party guests on which rules to break.
	\item Assign each party guest a drink.
\end{itemize}

\subsubsection*{OC Instructions}
At least two hours before the test:
\begin{itemize}
	\item Select and announce the robot start location.
	\item Select and announce which room is forbidden.
\end{itemize}

% \newpage
\subsection*{Score sheet}
\input{scoresheets/SticklerForRules.tex}

% Local Variables:
% TeX-master: "Rulebook"
% End:

