\documentclass[a4paper]{article}
\usepackage[utf8x]{inputenc}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}

\usepackage{url}
\usepackage{graphicx}
\usepackage{color}
\usepackage{tabularx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{epstopdf}
\usepackage{subfig}
\usepackage{float}
\usepackage{amsmath}
\usepackage{wrapfig}
\usepackage{titlesec}
\usepackage{xfrac}

\newcommand{\quotes}[1]{``#1''}
\newcommand{\textbi}[1]{\textbf{\textit{#1}}}
\newcommand{\sectionbreak}{\clearpage}
\newcommand{\subsectionbreak}{\clearpage}

\begin{document}

\section{Introduction}
\section{Concepts behind the competition}
\section{General rules \& Regulations}
\section{Setup and preparation}

\section{Tests in Stage I}

\begin{itshape}
All ability and integration tests in Stage I grants 15 points and are performed 3 times. The total score for each of this tests is the average of the best two performances (still to be discussed, perhaps taking only the top 1 or --unlikely-- global average).

Open/Demo Challenge and RoboZoo are special cases. Those tests grant up to 10 points each, and have no changes from previous years. In case of Open/Demo Challenge (most likely is going to be a focused Demo Challenge), scoring will be redefined.
\end{itshape}

\input{GPSR}

\input{Manipulation}

\input{Navigation}

\subsection{Open/Demo Challenge}

\input{PersonRecognition}

\subsection{RoboZoo}

\input{SpeechRecognition}

\section{Tests in Stage II}

\begin{itshape}
All ability and integration tests in Stage II grants 25 points and are performed only once. Some tests --like Wake-me-up Test-- have optional tasks that grant additional points when performed correctly, clean and fast. TC must be informed if a team is planning to perform any of the optional tasks. No additional time is given while performing optional tasks.
\end{itshape}

\input{Restaurant}

\input{RoboNurse}

\input{WakeMeUp}

\section{Finals}

\end{document}