\chapter{Robo-Nurse diseases and symptoms list}

The following section presents the list of diseases an their symptoms to be used during the \textit{Robo-Nurse test}. Note that the list of symptoms is not extensive nor has been normalized in order to allow the teams to perform their own research on medical diagnosis.

\section{Disease list (by alphabetic order)}

\begin{itemize}

\item \textbf{Acid reflux:} Heartburn (acid indigestion), regurgitation (wet burp), burping, nausea after eating, stomach fullness or bloating, upper abdominal pain and discomfort. Treatment: anti-acid.

\item \textbf{Anemia:} Easy fatigue and loss of energy, unusually rapid heart beat (particularly with exercise), shortness of breath and headache (particularly with exercise), difficulty concentrating, dizziness, pale skin, leg cramps, insomnia, hunger for strange substances such as paper, ice, or dirt (a condition called pica); upward curvature of the nails (referred to as koilonychias), soreness of the mouth with cracks at the corners; tingling, \quotes{pins and needles} sensation in the hands or feet; lost sense of touch, a wobbly gait and difficulty walking, clumsiness and stiffness of the arms and legs. Treatment: take alimentary supplements, rest.

\item \textbf{Arthritis:} At the joint: pain, stiffness, swelling, redness, decreased range of motion. Treatment: medical advice, ice, pain killers.

\item \textbf{Back Pain:} Persistent aching or stiffness anywhere along your spine (from the base of the neck to the tail bone), sharp, localized pain in the neck, upper back, or lower back (especially after lifting heavy objects or engaging in other strenuous activity); chronic ache in the middle or lower back, especially after sitting or standing for extended periods; back pain that radiates from the low back to the buttock, down the back of the thigh, and into the calf and toes; inability to stand straight without having pain or muscle spasms in the lower back. Treatment: medical advice, pain killers.

\item \textbf{Common Cold:} Runny or stuffy nose, itchy or sore throat, cough, congestion, slight body aches, sneezing, watery eyes, low-grade fever, mild fatigue. Treatment: water, rest, chicken soup.

\item \textbf{Dandruff:} Flakes of skin on the scalp and hair (from small and white to large, greasy and yellow), head may feel tight and itchy, head may feel tingly, head may feel sore, red, flaky, greasy patches of skin. Special shampoo.

\item \textbf{Dehydration:} Dry and sticky mouth, sleepiness or tiredness, thirst, decreased urine output, few or no tears when crying, dry skin, headache, constipation, dizziness or lightheadedness. Treatment: water.

\item \textbf{Diarrhea:} Frequent, loose, watery stools; abdominal cramps, abdominal pain, fever, blood in the stool, bloating. Treatment: water, steamed vegetables, a cork.

\item \textbf{Flu:} Severe aches in joints and muscles, pain and tiredness around eyes, weakness or fatigue, warm, flushed skin and red, watery eyes; headache, dry cough, sore throat and runny nose. Treatment: water, rest, antiviral drug (Tamiflu).

\item \textbf{Headache: } Caused by alcohol (particularly red wine) certain foods (such as processed meats that contain nitrates, berries and nuts), changes in sleep or lack of sleep, poor posture, skipped meals, stress. Treatment: rest, aspirin, pain-killers.

\item \textbf{Heartburn:} Caused by strong drinks (alcohol, caffeine, carbonated water), acidic juices (grapefruit, orange, pineapple), drugs (aspirin, ibuprofen, Naproxen), acidic foods (tomatoes, grapefruit, oranges), fat-rich food (meat, chocolate), and smoking. Treatment: anti-acid.

\item \textbf{Heat Stroke:} Core body temperature above 105°F/45.5°C (Hallmark symptom), throbbing headache, dizziness and light-headedness, lack of sweating despite the heat, red, hot, and dry skin; muscle weakness or cramps, nausea and vomiting, rapid heartbeat, which may be either strong or weak; rapid, shallow breathing; behavioral changes such as confusion, disorientation, or staggering; seizures, unconsciousness. Treatment: Fan air over the patient's wet body, apply ice packs to the patient's armpits, groin, neck, and back, immerse the patient in a shower or tub of cool water, or an ice bath. Call ambulance.

\item \textbf{Hyperglycemia (high blood sugar):} Frequent urination, increased thirst,
blurred vision, fatigue, fruity-smelling breath, nausea and vomiting, shortness of breath, dry mouth, weakness, confusion, abdominal pain, headache. Treatment: medical assistance required, call for ambulance.

\item \textbf{Hypertension (high blood pressure):} Severe headache fatigue or confusion, vision problems, chest pain, difficulty breathing, irregular heartbeat, blood in the urine, pounding in your chest, neck, or ears. Treatment: medical assistance required, call for ambulance.

\item \textbf{Hypoglycemia (low blood sugar):} Sweating (almost always present, check for sweating on the back of neck at your hairline), nervousness, shakiness, and weakness; extreme hunger and slight nausea, dizziness and headache, blurred vision, a fast heartbeat and feeling anxious. Treatment: food.

\item \textbf{Hypotension (low blood pressure):} Dizziness or lightheadedness, unsteadiness, fainting (syncope), lack of concentration, dimming or blurred vision, nausea; cold, clammy skin; pale skin; rapid or shallow breathing, fatigue depression, thirst, weaknTuberculosisess.

\item \textbf{Migraine:} One day or two before: depressed or cranky, very happy, very awake, or full of energy; restless or nervous, very sleepy, thirsty or hungry, or may crave certain foods, or may not feel like eating. 30 minutes before: See spots, wavy lines, or flashing lights; have numbness or a \quotes{pins-and-needles} feeling in hands, arms, or face. Once it's started: Throbbing pain on one side (or even both sides) of the head, pain behind one of the eyes, moderate to very bad pain (it may be so bad that can't perform any of the usual activities), pain that gets worse with routine physical activity, nausea, vomiting, or both; pain that gets worse when around light, noise, and sometimes smells. Treatment: Pain-killers.

\item \textbf{Pharyngitis:} Red throat, sore throat, runny or stuffy nose, dry cough, hoarseness, redness of the eyes, fever, headache, joint pain and muscle aches, skin rashes, swollen lymph nodes (glands) in the neck, body ache and a general sick feeling generally sick feeling. Treatment: rest, ibuprofen, warm liquids, medical advice to get antiviral or antibiotic treatment.

\item \textbf{Pneumonia:} Cough (often producing mucus, also called sputum, from the lungs), mucus may be rusty or green or tinged with blood, fever (which may be less common in older adults), Shaking, \quotes{teeth-chattering} chills, fast, often shallow, breathing and the feeling of being short of breath; chest wall pain that is often made worse by coughing or breathing in, fast heartbeat, feeling very tired or weak, nausea and vomiting, shortness of breath, little mucus when coughing, diarrhea.Treatment: rest, ibuprofen, warm liquids. Medical assistance required.

\item \textbf{Premenstrual syndrome:} Tension or anxiety, sad or depressed mood, crying spells, mood swings and irritability or aggression or anger; appetite changes and food cravings, insomnia, social withdrawal, poor concentration, joint or muscle pain, headache, fatigue, weight gain related to fluid retention, abdominal bloating, breast tenderness, acne flare-ups, constipation or diarrhea. Treatment: ibuprofen, antispasmodic, warm liquids.

\item \textbf{Ringworm: }. On the scalp: dry, brittle hair or hair loss in patches; severe itching, red-ringed patch of small blisters or scaly skin. On the body: red-ringed patch of small blisters or scaly skin, severe itching is sometimes present Treatment: Apply ice to reduce itching and call medic to get prescriptive medicine.

\item \textbf{Scabies:} Intense itching (especially at night), a pimple-like rash, scales or blisters, sores caused by scratching. Treatment: Call medic to get prescriptive medicine. Take antihistamine pills and apply hydrocortisone cream after medical diagnosis.

\item \textbf{Sinusitis:} Pain and pressure in the face along with a stuffy or runny nose (main symptoms), yellow or greenish discharge from nose, headache, yellow or greenish discharge from the nose or down the back of the throat, bad breath, stuffy nose, cough that produces mucus, fever, tooth pain, reduced sense of taste or smell.Treatment: Drink plenty of fluids, apply moist heat (using a hot, damp towel or gel pack) for 5 to 10 minutes, breathe warm, moist air (from a steamy shower, a hot bath, or a sink filled with hot water).

\item \textbf{Sunburn:} Skin turns red and hurts, swelling and sunburn blisters (sever burn) feel like you have the flu (feverish, with chills, nausea, headache, and weakness). Treatment: Drink plenty of water, apply cold compresses , take nonsteroidal anti-inflammatory drugs, like ibuprofen or Naproxen, gently rub on a cream or gel containing menthol, camphor or aloe.

\item \textbf{Sun Poisoning:} Skin redness and blistering, pain and tingling, swelling, headache, fever and chills, nausea, dizziness, dehydration. Treatment: Get out of the sun, take a cool (not cold) shower or bath or apply cool compresses, drink extra fluids for a few days, take ibuprofen or acetaminophen to relieve pain, use aloe gel or a moisturizer, completely cover sunburned areas when going outside.

\item \textbf{Tuberculosis:} Coughing that lasts three o symptomsr more weeks, coughing up blood, chest pain, or pain with breathing or coughing; unintentional weight loss, fatigue, fever, night sweats, chills, loss of appetite. Treatment: Drink plenty of fluids, eat healthy food. Quarantine: medical assistance required, call for ambulance.

\item \textbf{Urticaria:} Swollen, pale red bumps or plaques (wheals) on the skin, itching, burning or stinging. Treatment: Apply cool compresses or wet cloths to the affected areas, antihistamine.

\end{itemize}
