%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%          $Id: Rulebook.tex 2014-12-12 balkce $
%%    author(s): RoboCupAtHome Technical Committee(s)
%%  description: introduction to RoboCupAtHome
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt, twoside, openright, a4paper, chapterprefix]{scrbook}
\usepackage[inner=2.5cm, outer=2.5cm, top=4cm, bottom=4cm]{geometry}

%%% PACKAGES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{./setup/packages.tex}
\usepackage[titletoc]{appendix}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{gensymb}
\setlist{noitemsep}

%%% SubfigureSetup %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\renewcommand{\subfigtopskip}{5pt}        % default is 10pt
%\renewcommand{\subfigbottomskip}{5pt}     % default is 10pt
%\renewcommand{\subfigcapskip}{3pt}        % default is 10pt
%\renewcommand{\subfigcapmargin}{7pt}      % default is 10pt

%%% TweakList-Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\itemhook}{%                 % modify itemize-spacing
  \setlength{\topsep}{2pt}%
  \setlength{\partopsep}{1pt}%
  \setlength{\itemsep}{-1pt}%
}
\renewcommand{\enumhook}{%                 % modify enumerate-spacing
  \setlength{\topsep}{2pt}%
  \setlength{\partopsep}{1pt}%
  \setlength{\itemsep}{-1pt}%
}
\renewcommand{\descripthook}{%             % modify description-spacing
  \setlength{\topsep}{2pt}%
  \setlength{\partopsep}{1pt}%
  \setlength{\itemsep}{-1pt}%
}

\setkomafont{title}{\normalfont}
\setkomafont{sectioning}{\normalfont\bfseries}
\addtokomafont{caption}{\small}
\setkomafont{captionlabel}{\small\bfseries}
\setkomafont{descriptionlabel}{\normalfont\bfseries}
\renewcommand*{\chapterformat}{\LARGE{Chapter \thechapter}}

%%% MACROS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{./setup/active_version.tex}
\graphicspath{{\YEAR/}{./images/}}
\input{./setup/macros.tex}
\input{./setup/abbrevix.tex}



\makeindex                                % generate index
\makeabbex                                % generate abbreviations

%%% DOCUMENTINFO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hypersetup{
  pdftitle     = {RoboCup@Home Rules and Regulations},
  pdfsubject   = {RoboCup@Home Rulebook},
  pdfauthor    = {RoboCup@Home Technical Committee},
  pdfkeywords  = {RoboCup, @Home, Rules, Competition},
  colorlinks   = true,
  anchorcolor  = blue,
  linkcolor    = blue,
  urlcolor     = blue, 
}

%%% HEADINGS & PAGE STYLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\footline}{RoboCup@Home Rulebook / \rulebookVersion}
\pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{\chaptername\ \thechapter. \ #1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection \ #1}{}\renewcommand{\currentTest}{#1}}
\fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[RE]{\sffamily\rightmark}
\fancyhead[LO]{\sffamily\leftmark}
\fancyfoot[C]{\scriptsize \sffamily \footline{}}
\fancypagestyle{plain}{
        \fancyhf{}
        \fancyhead[LE,RO]{\thepage}
        \fancyhead[RE]{\sffamily\rightmark}
        \fancyhead[LO]{\sffamily\leftmark}
        \fancyfoot[C]{\scriptsize \sffamily \footline{}}
		\renewcommand{\headrulewidth}{0.5 pt}
}
\fancypagestyle{empty}{
        \fancyhf{}
        \fancyhead{}
        \fancyfoot[C]{\scriptsize \sffamily \footline{}}
		\renewcommand{\headrulewidth}{0 pt}
}

\newcommand{\quotes}[1]{``#1''}
\newcommand{\textbi}[1]{\textbf{\textit{#1}}}
%\newcommand{\sectionbreak}{\clearpage}
%\newcommand{\subsectionbreak}{\clearpage}


%%%%%%%%%%%%%%%%%%%\renewcommand{%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input{./pages/titlepage}

\pagestyle{empty}
\input{./pages/acknowledgments}
\clearpage

\pagestyle{empty}
\tableofcontents
\clearpage

\pagestyle{plain}

\input{Introduction}

\input{CompetitionConcepts}

\input{GeneralRules}

\input{Setup}

\chapter{Tests in Stage I}
\label{chap:stage_I}

\begin{itshape}
\iterm{Stage~I} comprehends five \textbf{ability tests} and an \textbf{integration test} along with an open demonstration for the audience. 
Each ability test is designed to evaluate the average performance of the robot in one particular skill, providing data for benchmarking. 
Meanwhile, the integration test has been designed to evaluate how this abilities work together while solving a common task.

The total score for ability and integration tests is the average of the best two performances out of preferably three performances (given the time constraints of a competition).
The point of this is the both elimate good and bad luck for the robots/teams and to get a more objective view of the performance, 
  not to give teams time to tweak the robot between test performances. 

\iterm{Following and Guiding} (demonstration for the audience) goes out of the arena and into the venue between the audience. 

\end{itshape}

\subsection*{Scheduling}
For maximal efficiency, teams will be scheduled interleaved: 
  Team A does an attempt while team B sets up their robot. When A is done, it moves out the way for team B, then B attempts while A sets up the robot again etc.

The preparing team should prepare their robot close to the place of the test, but not interfere with the performing robot.
Prepared robots must wait at this preparation location until commanded to start the test.
When commanded to start, the robot must move automatically beyond this point. 

Robot should be ready to start the next attempt to the same test as fast as possible: 
  when the performing robot is done with a attempt, the next robot must be ready to go with the start of a button or a voice command.

\newpage
\input{tests/StoringGroceries}

\newpage
\input{tests/CocktailParty}

% \newpage
% \input{tests/Navigation}

\newpage
% Speech and Person Recognition
\input{tests/SPR}

\newpage
\input{tests/HelpMeCarry}

\newpage
\input{tests/GPSR}

\chapter{Tests in Stage II}
\label{chap:stage_II}

\begin{itshape}
All ability and integration tests in \iterm{Stage~II}  are performed only once. Some tests have optional tasks that grant additional points when performed correctly, clean and fast. The \iaterm{Technical Committee}{TC} must be informed if a team is planning to perform any of the optional tasks. Unless explicitly stated otherwise, no additional time is given while performing optional tasks.

In the \iterm{Open Challenge} the robot must be able to show to the \iaterm{Technical Committee}{TC} the achievements on the main research line of its own team. This test grants up to 250 points.

\section{Robot \& team cooperation}
We encourage robots and teams to work together when performing challenges.
For scoring, points are awarded per subtask. The robot (and thus team) performing the subtask gets the points.
For example, in the Restaurant-challenge, if one robot of team A can take the order and another robot of team B delivers the order, then the points for taking the order go to team A, while the points for delivering go to team B. 
Of course, team A \& B can both perform the challenge in their own turn.

\end{itshape}

\newpage
\input{tests/SetATableTidyUp}

\newpage
\input{tests/TourGuide.tex}

\newpage
\input{tests/OpenChallenge}

\newpage
\input{tests/Restaurant}

\newpage
\input{tests/EEGPSR}

\newpage
\input{tests/Finals}

\input{Appendices}

\printabx
\printidx

\end{document}
