\section{Clean the Table}
\label{test:clean-the-table}
The robot cleans up a table after a meal. All dishes and cutlery must be placed inside the dishwasher and all food related objects must be stored in the correct place. \\

\noindent \textbf{Main goal:} Clean up all the objects on the table. Tableware and cutlery have to be placed inside the dishwasher and food objects have to be placed on the cabinet grouping them by category or similarity. \\

\noindent \textbf{Optional goals:}
\begin{enumerate}[nosep]
	\item Opening the dishwasher door
	\item Pulling out the dishwasher rack
	\item Placing the items in the dishwasher correctly
	\item Placing a dishwasher tab inside the dishwasher
	\item Placing the trash inside the trash bin
\end{enumerate}

\subsection*{Focus}
\emph{Object perception}, \emph{manipulation in narrow spaces}, and \emph{task planning}.

% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Setup
% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Setup}
\begin{itemize}[nosep]
	\item \textbf{Locations:}
		\begin{itemize}
			\item \textbf{Start Location:} Before the test, the robot waits outside the Arena and navigates to the testing area when the door is open.
			\item \textbf{Test location:} This test takes place in the kitchen.
		\end{itemize}
	\item \textbf{People:}
		\begin{itemize}
			\item No people are involved in the test, unless the robot requires human assistance.
		\end{itemize}
	\item \textbf{Furniture:}
		\begin{itemize}
			\item \textbf{Dishwasher:} A dishwasher is located close to the dining table.
			\item \textbf{Tray:} A plastic tray, which may have other tableware and cutlery placed inside, is located either on top of the dishwasher or on one of the racks. Objects can be placed either in the dishwasher rack or in the tray, based on the team's choice.
			\item \textbf{Cabinet:} The cabinet, located in the kitchen, contains objects arranged in groups (either by category or likeliness) on different shelves and sides of the shelf (left or right).
			\item \textbf{Trash bin:} A trash bin is located in the kitchen.
		\end{itemize}
	\item \textbf{Objects:}
		\begin{itemize}
			\item \textbf{Table setting:} The table has a total of nine objects disposed in a typical setting for a meal for one person.
			The object distribution is as follows:
			\begin{itemize}[nosep]
				\item\textit{Cutlery}: Any two objects (fork, knife, or spoon).
				\item\textit{Tableware}: Any three objects (except cutlery), at least one of which is a dish.
				\item\textit{Food}: Any four food objects (can be any object from: foods, drinks, fruits or snacks).
			\end{itemize}
			\item \textbf{Dishwasher tab:} The tab can be found at a location that is announced before the test and should be autonomously placed inside the tab slot in the dishwasher.
			\item \textbf{Trash Item:} The trash item is one of the four food objects on the table. The trash item belongs to a class of objects, that will be announced before the test (example: the class of objects used as trash for this test is 'drinks')
		\end{itemize}
\end{itemize}


% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Procedure
% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Procedure}
\begin{enumerate}[nosep]
	\item \textbf{Dishwasher door and rack}: Half an hour before the test, the team informs the referees:
		\begin{itemize}
			\item whether objects will be placed in the dishwasher rack or in the tray
			\item whether the dishwasher door should be closed and, if the door is open, whether the rack should be pushed in
		\end{itemize}
	\item \textbf{Test start:} The robot moves to the kitchen when the arena door is open.
	\item \textbf{Table clean up:} The robot cleans the table by putting: the cutlery and tablware items inside the dishwasher and the food either on the cabinet or the trash bin.
\end{enumerate}


% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Additional Rules
% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Additional Rules and Remarks}
\begin{enumerate}[nosep]
	\item \textbf{Safe placing:} Objects must be placed with care, namely the robot should place rather than throw or drop objects.
	\item \textbf{Dishwasher:} The team decides whether the robot will place the objects in the dishwasher's rack or in the plastic tray.
	\item \textbf{Dishwasher door:} The dishwasher door is open and with the racks pulled out by default.
	The team leader can, however, request the dishwasher to be closed for bonus points. If the robot fails to open the door, it must clearly state this and request the referee to open the door.
	\item \textbf{Correct dishwasher item placement:} The items should be placed in the rack/tray correctly, namely in the location and in a manner as a person would put them.
	\item \textbf{Incorrect cabinet shelf categorization:} The score is reduced if an object is stored on the cabinet, but not on a shelf side with similar objects; this reduction is applied per incorrectly stored object.
	\item \textbf{New category:} Objects that do not semantically belong to any of the categories represented on the cabinet shelves should be grouped together on a new shelf.
	\item \textbf{Deus ex Machina:} The scores are reduced if human assistance is received, in particular:
	\begin{itemize}[nosep]
		\item pointing to an object or telling the robot where an object is
		\item handing an object over to the robot
		\item telling or pointing out to the robot where to place an object
		\item moving an object instead of the robot
	\end{itemize}
	\item \textbf{Communicating Perception}: The robot must clearly communicate its perception to the referee.
	Pointing at the object or attempting to pick it up is sufficent. When using visualization, make sure the robot 
	tells the referee where to look and make the visualization easily accesible. 
	If the team wants to utilize bounding boxes make sure \textbf{only} one object with a bounding box is shown 
	at a time so the referee is easily able to check and verify. Also make sure the surrounding scene is visible, i.e.
	just showing a cropped bounding box is not enough.
\end{enumerate}

\subsection*{OC Instructions}

During the \SetupDays:
\begin{itemize}
	\item Provide official cutlery and tableware for training.
\end{itemize}

At least two hours before the test:
\begin{itemize}
	\item Announce which table and cabinet will be used in the test.
	\item Announce the predefined location of the dishwasher tab.
	\item Announce the class of objects to be trash objects.
\end{itemize}


\subsection*{Referee Instructions}

The referee needs to:
\begin{itemize}
	\item Place objects on the table (two pieces of cutlery, three pieces of tableware and four food objects, where one of the food objects is from the class defined as trash.)
	\item Place the plastic tray on the dishwasher or on a rack, as requested by the team.
	\item Place objects in the cabinet, grouping them by category or likeliness.
\end{itemize}

\subsection*{Score sheet}
\input{scoresheets/CleanTable.tex}

% Local Variables:
% TeX-master: "Rulebook"
% End:
