\section{Clean Up [House Holder]}
The robot has to clean the room from the house it has been told to clean up.

% \subsection{Focus}
% This test focuses on object perception, manipulation, and planning.

\subsection{Main Goal}
Upon entrance, the robot requests the operator which room shall be cleaned.
All misplaced known objects found in this room must be taken to their predefined locations and unknown objects thrown to the trash bin.

\noindent\textbf{Reward:} 500pts (100pts per object).

\subsection{Bonus rewards}
\begin{enumerate}[nosep]
	\item Opening the entrance door (200pts)
	\item Moving a \emph{tiny} object (100pts)
	\item Moving a \emph{heavy} object (100pts)
	\item Leaving the arena (100pts)
\end{enumerate}


\subsection{Setup}
\begin{itemize}[nosep]
	\item \textbf{Location:} A random room in the arena.

	\item \textbf{Objects:} There are 5 objects placed at random locations in the room.
	Objects can be anywhere, including the floor, seats, and on furniture.
	All objects are visible from at least 1.0m distance (i.e. no occlusions) and have the following distribution:
	\begin{itemize}[nosep]
		\item\textit{Known objects}: Any two regular and two alike objects.
		\item\textit{Unknown objects}: One unknown object at grasping distance (i.e. no decorations).
	\end{itemize}
\end{itemize}

\subsection{Additional rules and remarks}
\begin{enumerate}[nosep]
	\item \textbf{Deus ex Machina:} Score reduction for requesting human assistance is applied per object as follows:
	\begin{itemize}[nosep]
		\item \textbf{Verbal object location disclosure:} Telling the robot where an object can be found causes a reduction of 30\% in scoring for that particular object.

		\item \textbf{Pointing at an object location:} Pointing at an object to be picked up causes a reduction of 40\% in scoring for that particular object.
		
		\item \textbf{Guiding to an object location:} Guiding the robot nearby the location where an object can be found causes a reduction of 20\% in scoring for that particular object.

		\item \textbf{Revealing placement location:} Telling the robot where the object should be placed or the object's category causes a reduction of 30\% in scoring for that particular object.

		\item \textbf{Object transport and handover:} Having a human physically interacting with an object causes a reduction of 60\% in scoring for that particular object.
	\end{itemize}
	
	\item \textbf{Heavy and tiny objects:} Objects used in this test are lightweight and average-sized.
	The team leader can, however, request a tiny and a heavy object to be used and score additional points for picking them.
	
	\item \textbf{Bin:} Objects must be placed inside the bin, not thrown or dropped.	
\end{enumerate}

\subsection{Referee instructions}
The referee needs to
\begin{itemize}
	\item Place the objects in the room.
	\item Recover disposed objects from the bin.
\end{itemize}

\subsection{OC instructions}
2 hours before the test:
\begin{itemize}
	\item Announce the location where the robot will be instructed.
\end{itemize}