\section{Farewell [Party Host]}
It's raining outside. The robot takes tired guests to their cab/über. Ladies go first.

% \subsection{Focus}
% This test focuses on human detection and recognition, safe navigation and human-robot interaction with unknown people.

\subsection{Main Goal}
Some guests are tired, so they call the robot to retrieve their coat.
It's raining outside and there is only one umbrella, so the robot takes the guests one by one to their cab and returns with the umbrella.

\noindent\textbf{Reward:} 600pts (300pts per guest).

\subsection{Bonus rewards}
\begin{enumerate}[nosep]
	\item Delivering the right coat (150pts each, max 300pts)
	\item Identifying the female calling person and escorting her first (100pts)
\end{enumerate}


\subsection{Setup}
\begin{itemize}
	\item \textbf{Location}: The test takes place inside and outside the arena.
	Guests are in the living room.

	\item \textbf{Start Location}: The robot starts inside the arena at a predefined location near the entrance door.

	\item \textbf{Guests}: Initially there are five people in the living room, three sitting and two standing.
	At least two guests are female.
	All guests have a name and coat color assigned.

	\item \textbf{Calling guests:} Only two guests are willing to leave. Both guests, male and female, will call the robot by waving or shouting at the same time.
\end{itemize}

\subsection{Additional rules and remarks}
\begin{enumerate}[nosep]
	\item \textbf{Partial scoring:} The main task allows partial scoring.
	Robot score per guest upon reentering the arena.

	\item \textbf{Deus ex Machina:} Score reduction for requesting human assistance is applied per guest as follows.
	\begin{enumerate}[nosep]
		\item \textbf{Indicating leaving guest:} Telling the robot which guest is leaving (e.g. verbally or pointing at her) causes a reduction of 10\% in scoring for that particular guest.

		\item \textbf{Guiding to the cab location:} Guiding the robot where the Cab Driver is standing causes a reduction of 40\% in scoring for that particular guest.

		\item \textbf{Guiding back to the house:} Guiding the robot back to the house causes a reduction of 40\% in scoring for that particular guest.

		\item \textbf{Coat handover:} Handing over a coat to the robot (i.e. no hook off) causes a reduction of 50\% of the scoring bonus.
	\end{enumerate}

	\item \textbf{Kicking out guests:} Non-calling guests will refuse to leave the house. The robot must confirm that the guest was calling and willing to leave.
	
	\item \textbf{Identifying the Cab:} There will be no cab, taxi, or any other vehicle parked outside the arena.
	The cab location is identifiable by the \emph{Cab Driver}.

	\item \textbf{Cab Driver:} The cab driver is an unknown person waving, wearing high-visibility clothing (e.g. fluorescent vest), and standing under an open umbrella.
	The distance between the cab driver and the arena cannot exceed 15m.
	
	\item \textbf{Delivering coats:} Coats are hanging on a coat rack near the exit door.
	The robot is supposed to autonomously hook off the coats and bring them back to the right person.
\end{enumerate}


\subsection{Referee instructions}

The referees need to
\begin{itemize}
	\item Select at least 5 volunteers and assign them name and a color coat.
	\item Choose the calling people.
	\item Relocate the Cab Driver
	\item Mind the robot when it goes outside the arena.
\end{itemize}

\subsection{OC instructions}
During Setup days
\begin{itemize}
	\item Provide coats for training
	\item Provide umbrella for training
	\item Provide Cab Driver's high-visibility clothing for training
\end{itemize}

2h before test:
\begin{itemize}
	\item Select and announce the robot starting point
	\item Help to relocate the Cab Driver
\end{itemize}

% \newpage
% \subsection{Score sheet}
% \input{scoresheets/Receptionist.tex}
