\section{Find My Mates [Party Host]}
\label{test:find-my-mates}

\subsection*{Description}
    The robot collects some information about various party guests for the operator, who only knows the names of the guests.

\textbf{Main goal:}
    Report to the operator the description and location of at least two party guests.

\textbf{Optional goal:}
\begin{enumerate}[nosep]
	\item Reporting the location and description of a third guest.
\end{enumerate}

\subsection*{Focus}
This test focuses on \SysI{}, \HRI{}, \PerDet{}, \PerRec. 

\subsection*{Setup}
\begin{itemize}
	\item \textbf{Location}: This test takes place inside the \Arena{} in a predefined room (e.g. living room).
	\item \textbf{People}: There are 4 people distributed along the room.
\end{itemize}

\subsection*{Procedures}
\begin{enumerate}
	\item The referee requests the team to move the robot to the start location.
	\item The referee gives the start signal and starts the timer.
	\item The team leaves the area after the start signal.
	\item A TC member follows the robot ready to press the emergency stop button. 
	\item Robot finds and reports description and location of two guests.
	\item \textbf{Optionally,} robot reports descriotion and location of the third guest.
\end{enumerate}

\subsection*{Additional Rules and Remarks}
\begin{enumerate}[nosep]
	\item \textbf{Reporting:} Points are scored only when the robot goes back to the operator and delivers the report on time.

	\item \textbf{Description of a person:} The description of each guest should be unique, i.e. not shared with any other guest. This may include clothing, age, height, complexion, skin or hair color, gender, etc.

	\item \textbf{Location of a person:} A relative location based on the surroundings (e.g. sitting on the couch, standing beside the lamp, etc.).

	\item \textbf{Deus ex Machina:} Score reduction for human assistance is applied per guest as follows:

		\begin{itemize}
		    \item Waving to the robot in order to be found
			\item Telling the robot where a person is located
			\item Approaching the robot (e.g. walking and standing in front of it)
		\end{itemize}

\end{enumerate}

\subsection*{Instructions}

\textbf{To Referees}
The referees need to:
\begin{itemize}
	\item Assign names and locations to the all guests.
	\item Make sure that the guests stay at their designated locations during the test.
\end{itemize}

\textbf{To OC}

2h before test:
\begin{itemize}
	\item Announce the location where the robot will be instructed.
	\item Announce the room in which the test will take place.
\end{itemize}

% \newpage
\subsection*{Score sheet}
\input{scoresheets/FindMyMates.tex}

