\section{Functional Grasping Challenge}\label{test:functional-grasping-challenge}
The robot assists with laundry by retrieving clothes from a washing machine and folding them neatly on a table. This test evaluates deformable object manipulation, appliance interaction, and task sequencing.\\

\noindent \textbf{Main goal:} Transport clothes to a table, and fold them.\\

\noindent \textbf{Optional goals:}
\begin{enumerate}[nosep]
    \item Opening the washing machine door
    \item Retrieving clothes from inside the washing machine
    \item Using a laundry basket for transportation
    \item Folding multiple pieces of clothing and stacking them
\end{enumerate}

\subsection*{Focus}
\emph{Deformable object manipulation}, \emph{bimanual grasping}.

% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Setup
% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Setup}
\begin{itemize}
    \item \textbf{Locations:}
        \begin{itemize}
            \item \textbf{Start location:} Before the test, the robot waits outside the \Arena{} and navigates to the laundry area when the door is open.
            \item \textbf{Test locations:} The testing area contains a washing machine, a folding surface nearby, and a laundry basket.
        \end{itemize}
    \item \textbf{People:}
        \begin{itemize}
            \item No people are involved in the test, unless the robot requires human assistance.
        \end{itemize}
    \item \textbf{Furniture:}
        \begin{itemize}
            \item \textbf{Laundry basket:} A lightweight basket requiring two arms to carry, placed near the washing machine. The basket already has 6--8 pieces of clothing placed inside.
            \item \textbf{Washing machine:} Positioned with its door closed at the start. Clothes are placed inside. There are 2--4 pieces of clothing in the washing machine.
            \item \textbf{Table:} Positioned near the washing machine. Used as the folding surface.
        \end{itemize}
    \item \textbf{Objects}:
        \begin{itemize}
            \item \textbf{Clothes:} A set of 8--12 pieces of laundry made from cloth or other deformable fabric.
        \end{itemize}
\end{itemize}

% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Procedure
% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Procedure}
\begin{enumerate}[nosep]
    \item \textbf{Location announcement:} At least two hours before the test, referees announce which washing machine and table will be used, along with the approximate location of each.
    \item \textbf{Test start:} The robot enters the testing area once the arena door is opened.
    \item \textbf{Retrieving laundry:} The robot retrieves the clothes from the laundry basket or directly from the washing machine and places them on the table.
    \item \textbf{Folding:} The robot attempts to fold at least one piece of clothing neatly.
\end{enumerate}

% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Additional Rules
% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Additional rules and remarks}
\begin{enumerate}
    \item \textbf{Laundry Types:} The laundry will consist exclusively of T-shirts.
    \item \textbf{Cloth placement:} Clothes must be placed on the table before folding. Folding on the floor is not allowed.
    \item \textbf{Folding quality:} Folding is evaluated by neatness and whether the cloth is flattened and stacked.
    \item \textbf{Multiple items:} Additional points are awarded for folding multiple pieces of clothing and stacking them.
    \item \textbf{Human Assistance:} Scores are reduced if human assistance is received, in particular for:
    \begin{itemize}
        \item opening the washing machine door
        \item handing clothes to the robot
        \item \textbf{Folding:} Penalties are proportional to the amount of help provided:
        \begin{itemize}[nosep]
            \item Minimal help (e.g., smoothing wrinkles, stabilizing cloth): small penalty (~100 points).
            \item Partial folding (e.g., folding one half or aligning edges): moderate penalty (~200 points).
            \item Major help (e.g., completing entire fold/stack): maximum penalty.
        \end{itemize}
    \end{itemize}
\end{enumerate}

\subsection*{OC Instructions}
At least two hours before the test:
\begin{itemize}
    \item Announce which washing machine and table will be used.
\end{itemize}

\subsection*{Referee Instructions}
The referee needs to:
\begin{itemize}
    \item Ensure the washing machine and basket contains the laundry before the test begins.
    \item Close the washing machine door at the start.
    \item Verify that the folding table is clear before the test.
\end{itemize}

% \newpage
\subsection*{Score sheet}
\input{scoresheets/FunctionalGraspingChallenge.tex}
