\section{Human Robot Interaction Challenge}
\label{test:human-robot-interaction-challenge}

\subsection*{Description}
The robot is working as a receptionist at a party. The robot has to take two new guests to the living room, offer a free place to sit and introduce them to eachother. The second guest brings a bag for the robot to carry.\\
    
\textbf{Main goal:}
    The robot welcomes and assists two newcomers at a party and offering them a seat, and maintaining appropriate gaze direction during conversation (at person speaking, direction of navigation). The second guest brings a bag to be placed somewhere in the house. 

% \vspace{-5pt}
\textbf{Optional goals:}
\begin{enumerate}[nosep]
	\item Detect doorbell sound as a signal that a guest has arrived.
	\item Open the entrance door for each arriving guest.
	\item Visually describe the first guest to the second guest before reaching the living room.
	\item Understand each guest's name and favorite drink without asking any confirmation or correction questions (non-essential questions).
\end{enumerate}

\subsection*{Focus}
\emph{\SysI{}}, \emph{\HRI{}}, \emph{\PerDet{}}, \emph{\PerRec{}}
% human detection and recognition, safe navigation and human-robot interaction with unknown people.

\subsection*{Setup}
\begin{itemize}
	\item \textbf{Location}: 
	\begin{itemize}
	\item The test takes place in the living room.	
	\item The robot starts inside the \Arena{} at a predefined location near where guests are sitting.
	\item \textbf{Entrance:} The entrance door is open by default. The team leader can request it to be closed to allow the robot to earn additional points by opening it for the guests.
	\end{itemize}
	
	\item \textbf{People:} 
	\begin{itemize}
	\item \textbf{Arriving Guests:} Both guests have a name and a favorite drink. An arriving guest will wait by the door, and the robot has to move to meet guests by the door. A guest will not move inside the house until the robot has initiated conversation. It is not allowed to instruct guests to move in front of the robot to recognize the guest and start the conversation. The robot is the one that must approach the guest. Guests have to be guided to the living room where the robot will offer a free place to sit and introduce the guests to each other. Each guest will arrive separately. 
	\item \textbf{Passive Guests:} A few individuals, including possibly spectators, can be anywhere in the arena — sitting or standing in relevant places, e.g., on the couch, near the seats, or in the area with the drinks.
	\end{itemize}

\end{itemize}

\subsection*{Procedure}
Both guests arrive separately. A doorbell will ring to signal the guest has arrived. 
The doorbell will only ring if the robot is waiting for a new guest at the starting position.
The robot either opens the door for the guest or meets them at the door.
It greets the guest and asks for their name and favorite drink.
The robot escorts the guests to the living room and offers a free seat. 
Once both guests are seated, the robot introduces them to each other. To introduce the two guests, the robot must (for both guests) look at a guest and state the other arriving guest name and favorite drink.
The second guest will bring a bag for the host. The robot should ask for the bag to be handed over and move to the host. The host is already waiting and instructs the robot to follow him/her. The host will move to a random place in the house and inform the robot it can drop the bag there.   
\begin{itemize}

	\item \textbf{Doorbell:} A doorbell sound will be played when a guest is by the door ready to be met. The doorbell sound will not be provided beforehand and may be any traditional doorbell sound. As an alternative, if no doorbell sound is available, the guest can knock on the door. Waiting for the doorbell is optional, robots can bypass it and directly meet the guest at the door. In order for the doorbell sound to be considered detected, the robot must be waiting at the starting position and react instantly to the sound.
	
	\item \textbf{Greeting guests:} The names of the guests can be any popular english names. The favorite drinks of the guests can be any english named popular drink (it may not be in the list of objects provided).
	The guest paces slightly to the left and right during the conversation with the robot. Other people might appear in the background. 
	
	\item \textbf{Looking at person:} The robot must look at the person it is talking to. Guests will move slightly to confirm the robot dynamically follows them with its gaze. Points for gaze tracking are awarded only if the robot continuously tracks the moving person.
	
	\item \textbf{Looking at direction of navigation:} The robot must look in the direction it is navigating. Persistently looking in an unrelated direction or at unrelated people during navigation results in a score deduction.
    
	\item \textbf{Seating People:} The robot must clearly indicate or point to a location or seat for each guest.

	\item \textbf{Switching Places:} After being seated, guests may switch seats.
	
	\item \textbf{Introductions:} When introducing guests, the robot must clearly identify the person being introduced and state their name and favorite drink. The robot must be looking at a guest and state the other arriving guest name and favorite drink. The robot must do this for both guests.
	Introducing two people means to introduce them to each other.
	
	\item \textbf{Non-Essential Questions:} If the robot does not ask any non-essential questions to help understand, confirm, or correct information, bonus points are awarded. 
		Questions such as "Did you say your name is James?" or "Is your favorite drink milk?" are considered non-essential questions. 
		However, asking a guest to repeat an answer because the robot could not hear is not considered a non-essential question.

	\item \textbf{Bag handover:} The robot must grab the bag from the second guest hand. If this is not possible, the robot can instruct the guest to place the bag smewhere in its structure 

	\item \textbf{Follow the host:} The host will be sitting down in the living room, the robot must inform the host it has a bag and ask for the host to provide guidence. 
	The robot should inform the operator when it is ready to follow the host. The operator walks naturally towards the designated bag drop location. When at the correct location, the robot will inform the robot it must place the bag on the floor.


\end{itemize}

\subsection*{Additional rules and remarks}
\begin{enumerate}[nosep]
	\item \textbf{Opening Door Timing:} The Time of the test only starts after the first person enters the arena or 1 minute after start signal.

	\item \textbf{Misunderstanding:} Not understanding the guests and asking them again is fine. Continuing with a wrong name or favorite drink causes a score reduction.
		
	\item \textbf{Partial Scoring:} The main task allows partial scoring per guest.

	\item \textbf{Additional Seating:} Referees may add chairs to the living room area.
	
	\item \textbf{Deus ex Machina:} Score reduction applies per guest as follows:
	\begin{itemize}[nosep]
		\item \textbf{Custom Operator:} Since the main focus of the test is HRI, no custom operator can be chosen.
		\item \textbf{Alternative HRI:} Using an alternative HRI to understand a guest causes a score reduction per information (name or favorite drink).
		\item \textbf{Recognizing People:} If the robot has to ask for help to identify people, the score is reduced. 
		\item \textbf{Bag handover:} If the robot has to ask the guest for help during handover, the score is reduced. 
		If the robot tells the guest to place the bag somewhere on its structure, no points are awarded for the handover.  

		\item \textbf{Follow the host:} Penalties apply if the robot loses the operator and needs help recovering. The following forms of assistance are penalized:
		\begin{enumerate}
		\item Natural interaction (e.g., waving and calling)
		\item Unnatural interaction (e.g., raising both hands and jumping)
		\item Returning in front of the robot to resume following.
		\item Physical contact (e.g., pulling the robot's hand)
		\end{enumerate}
	Penalties are only applied if the robot continues to score after the interaction. Penalties can be applied multiple times.

	\end{itemize}
\end{enumerate}


\subsection*{Instructions}

\subsubsection*{To Referee}

The referees need to:
\begin{itemize}
	\item Assign name and favorite drink to two volunteers.
	\item Arrange and rearrange people in the living room.
	\item Open the entrance door upon request from the robot.
\end{itemize}

\subsubsection*{To OC}


During setup day:
\begin{itemize}
	\item Announce the bag that will be used for handover.
\end{itemize}


At least two hours before test:
\begin{itemize}
	\item Announce the starting position.
	\item Recruit four volunteers: two as arriving guests and two as passive guests.

\end{itemize}

% \newpage
\subsection*{Score sheet}
\input{scoresheets/HumanRobotInteractionChallenge.tex}