\section{Onlooker [Housekeeper]}
Robot observes activities performed by an individual and reports them. 

\subsection{Main Goal}
Robot reports the sequence of activities performed by a person.

\noindent\textbf{Reward:} 500pts (100 pts per activity).

\subsection{Bonus rewards}
\begin{enumerate}[nosep]
	\item 500 pts for reporting the sequence of activities for the second person (100 pts per activity)
\end{enumerate}


\subsection{Setup}
\begin{itemize}
	\item \textbf{Location}: The test takes place in the living room.

	\item \textbf{Start Location}: The robot starts at a predefined location.

	\item \textbf{Persons}: There are two people. At the start, the main person to look for is standing, and the second person is sitting.
\end{itemize}

\subsection{Additional rules and remarks}
\begin{enumerate}[nosep]
	\item \textbf{Partial scoring:} The task allows partial scoring for each reported activity.
	
	\item \textbf{Activity List:} talk to someone, talk on a phone call, reading, writing, relaxing, walking, drinking, and using laptop.
	
	\item \textbf{Activities:}  In the first three minutes, both persons will perform five activities in a sequence (i.e., no overlap of activities) chosen from the above list.
	
	\item \textbf{Observation:} The robot can move around for the better observation but without interfering anyone in the house.
	
	\item \textbf{Reporting:} In the last two minutes, the robot should return to the start location and read the report loudly to the operator. An exmaple of report's format is \textit{`The main/second person talked on phone call, then walked, then drank, then talked to a person ...'}.
	
\end{enumerate}


\subsection{Referee instructions}

The referees need to
\begin{itemize}
	\item Select 2 volunteers.
	\item Assign one activity at the start to each person.
	\item Assign one activity every 30 seconds to both persons, till the fifth activity is assigned.
\end{itemize}

\subsection{OC instructions}

2h before test:
\begin{itemize}
	\item Select and announce the robot's starting point
\end{itemize}

% \newpage
% \subsection{Score sheet}
% \input{scoresheets/Receptionist.tex}
