\section{Play Chess [Party Host]}
\label{test:smoothie-chef}
The human plays chess against the robot.
The robot must observe the human and survive 5 moves or win sooner.

% We will need a chess board and chess pieces of a reasonable size and wieght. 

% \subsection*{Focus}
% The idea behind the test is that the robot understands the scene and current state
% and is able to perform complexe manipulation safely with a human nearby.
% this test can grow as manipulation, recognition and planning get faster and safer.
% in the future, we could have robots play multiple games at once or entire games against pro humans
% Object manipulation and scene understanding.

\subsection*{Main Goal}
Survive 5 moves of chess or win the game.

\noindent\textbf{Reward:} 750pts.


\subsection*{Bonus rewards}
\begin{enumerate}[nosep]
	% Not intended to be addressed in 2019
\end{enumerate}

\subsection*{Setup}
\begin{itemize}[nosep]
	\item \textbf{Location:} The test takes place at a table.

	\item \textbf{Start Location:} The robot starts outside the arena.
	When the door is open, it navigates to table.

	\item \textbf{Operator location:} The operator is sitting in front of the robot on the opposite side of the table.

\end{itemize}

\subsection*{Additional rules and remarks}
\begin{enumerate}
	\item \textbf{Deus ex Machina:} Score reduction is applied as follows:
	\begin{itemize}[nosep]
	\end{itemize}
\end{enumerate}

\subsection*{OC Instructions}
During Setup days
\begin{itemize}[nosep]
	\item Announce the chess set to be used.
\end{itemize}

2 hours before the test
\begin{itemize}[nosep]
	\item Announce the location of the table.
\end{itemize}

\subsection*{Referee instructions}
The referee needs to
\begin{itemize}[nosep]
	\item Sit at the table.
	\item Setup the Chess Set.
	\item Decide at random if the robot or human goes first.
\end{itemize}


% \newpage
\subsection*{Score sheet}
\input{scoresheets/SmoothieChef.tex}
