\section{Receptionist}
\label{test:receptionist}

\subsection*{\textcolor{red}{New Updates for v2026}}
	\begin{itemize}
	\item \textcolor{red}{Removed guest name had to be selected from a predetermined list of names -> Now is any popular english name.}
	\item \textcolor{red}{Removed favorite drink had to be selected from a predetermined list of objects (drinks) -> Now is any english named popular drink.}
	\item \textcolor{red}{Robots now have to check and inform the if the drink is not in the beverage area and move on with the task}
	\item \textcolor{red}{Robots have more freedom to choose when to ask for the favorite drink and interest of the guest.}
	\item \textcolor{red}{Guests will not meet the robot at starting point when they arrive, guests stay at the door. The robot has to meet them at the door.}
	\item \textcolor{red}{Added doorbell sound when guest has arrived.(Generic audio classification)}
	\item \textcolor{red}{Added small penalty for all non essential questions that robot asks to help understand or confirm information.}
	\item \textcolor{red}{Increased penalty for introduction with a wrong name, drink or interest.}
	\item \textcolor{red}{Decreased waiting time for door to be opened from 2mins to 1min.}
	\item \textcolor{red}{Alternative HRI penalty to understand guest, is now per information received and not overall. (should have been changed in last years updates)}
	\\
	\item \textcolor{red}{MISSING: add list of possible special cases. (guest is not facing to the robot and talks OR robot asks for name and person answers with favorite drink OR multiple guests at the same time and they answer in random order, ...)}
	\end{itemize}

\subsection*{\textcolor{red}{Notes for TC}}
	\begin{itemize}
	\item \textcolor{red}{The host name and favorite drink is not used for anything.}
	\item \textcolor{red}{Webservice can be used as an interrupt.}
	\end{itemize}

\subsection*{Description}
The robot has to take two new guests to the living room, \sout{to introduce them and offer a free place to sit.} \textcolor{red}{offer a free place to sit and introduce them to eachother.}\\
    
\textbf{Main goal:}
    The robot welcomes and assists two newcomers at a party, offering them a seat and maintaining appropriate gaze direction during conversation (at person speaking, direction of navigation).

% \vspace{-5pt}
\textbf{Optional goals:}
\begin{enumerate}[nosep]
	\item \textcolor{red}{Detect doorbell sound as a signal that a guest has arrived.}
	\item Open the entrance door for each arriving guest.
	\item Visually describe the first guest for the second guest before reaching the living room
	\item Identify similarities between the guests and the host and incorporate them into the conversation.
\end{enumerate}

\subsection*{Focus}
\emph{\SysI{}}, \emph{\HRI{}}, \emph{\PerDet{}}, \emph{\PerRec{}}
% human detection and recognition, safe navigation and human-robot interaction with unknown people.

\subsection*{Setup}
\begin{itemize}
	\item \textbf{Location}: 
	\begin{itemize}
	\item The test takes place in the living room.	
	\item The robot starts inside the \Arena{} at a predefined location.
	\item A table with drinks is prepared near the living room
	\item \textbf{Entrance:} The entrance door is open by default. The team leader can request it to be closed to allow the robot to earn additional points by opening it for the guests.
	\end{itemize}
	
	\item \textbf{People:} 
	\begin{itemize}
	\item \textbf{Host:} The host's name, favorite drink and interest will be announced before the test. The host is the only person sitting in the living room until the robot offers a free seat to another guest.
	\item \textbf{Arriving Guests:} Both guests have a name, favorite drink, and a interest. \sout{An arriving guest will either step in front of the robot or wait behind the door to step in if the door is closed.} \textcolor{red}{An arriving guest will wait by the door, robots have to move to meet guests by the door.} Guests have to be guided to the beverage area and then the living room where the robot will offer a free place to sit and introduce the guests to each other. Each of the guest will arrive separately. 
	\item \textbf{Passive Guests:} Other Guests: A few individuals, including possibly spectators, are standing in small groups of two or three, all over the arena but not covering relevant places e.g. the couch, seats or the area with the drinks.
	\end{itemize}

\end{itemize}

\subsection*{Procedure}
Both guests arrive separately. \textcolor{red}{As a signal that the guest has arrived, a doorbell will ring.}
The robot either opens the door for the guest or \sout{waits for them at the starting point.} \textcolor{red}{meets them at the door.}
It greets the guest and asks for their name.
\textcolor{red}{The favorite drink can be asked at any time, from the moment the guest enters the arena until the robot shows the beverage area.}
\textcolor{red}{The interest can be asked at any time, from the moment the guest enters the arena until the robot offers a seat in the living room.}
\sout{The robot finds out the interest of the guest at a freely chosen moment.}
The robot guides the guest to the beverage area, \sout{where it asks for their favorite drink} and checks if the guest favorite drink is available on the table. \sout{and where it stands.}
\textcolor{red}{If the favorite drink is available the robot must clearly show the guest where it is located on the table and tell the guest it may pick up the favorite drink. If not available, the robot must inform the guest that the drink is not available and move on.}
After showing the guest the beverage area, the robot escorts them to the living room and offers a free seat. 
Once both guests are seated, the robot introduces them to each other.
\begin{itemize}

	\item \textcolor{red}{ \textbf{Doorbell:} A doorbell sound will be played when a guest is by the door ready to be met. The doorbell sound will not be provided beforehand and can be any traditional doorbell sound. As an alternative, if no doorbell sound is available, the guest can knock on the door. Waiting for the doorbell is optional, robots can bypass it and directly meet the guest at the door. In order for the doorbell sound to be considered detected, the robot must be waiting at the starting position and react instantly to the sound.} 
	
	\item \textbf{Greeting guests:} \textcolor{red}{The names of the guests can be any popular english names. The favorite drinks of the guests can be any english named popular drink (it may not be in the list of objects provided). The interests of the guests can be any popular interest (e.g. sports, music, movies, hiking, gaming, cooking, traveling, ...).}
	The guest paces a little to the left and right during conversation with the robot. Other people might appear in the background. 
	
	\item \textbf{Looking at person:} The robot must look at the person it is talking to. Guests will move slightly to confirm the robot dynamically follows them with its gaze. Points for gaze tracking are awarded only if the robot continuously tracks the moving person.
	
	\item \textbf{Looking at direction of navigation:} The robot must look in the direction it is navigating. Persistently looking in an unrelated direction or at unrelated people during navigation results in a score deduction.
    
    \item \textbf{Smalltalk:} Ask each guest for one interest.
    
    \item \textbf{Finding the drink:} The robot shows both guest the drinking area where it will ask for their favorite drink and tell the guest if and where (left, center right is enough) that drink is available on the table. 
	
	\item \textbf{Seating People:} The robot must clearly point to a location or seat for each guest.

	\item \textbf{Switching Places:} After being seated, guests may switch seats.
	
	\item \textbf{Switching Places:} Guests may switch places after they were seated.
	
	\item \textbf{Introductions:} When introducing guests, the robot must clearly identify the person being introduced and state their name favorite drink and an interest. Introducing two people means to introduce them to each other.
\end{itemize}

\subsection*{Additional rules and remarks}
\begin{enumerate}[nosep]
	\item \textbf{Opening Door Timing:} The Time of the test only starts after the fist person enters the arena or \sout{2 mins} \textcolor{red}{1 minute} after start signal.

	\item \textbf{Misunderstanding:} Not understanding the guests and asking them again is fine. Continuing with a wrong name, drink or interest causes a score reduction per item.
		
	\item \textbf{Partial Scoring:} The main task allows partial scoring per guest.

	\item \textbf{Additional Seating:} Referees may add chairs to the living room area.
	
	\item \textbf{Deus ex Machina:} Score reduction applies per guest as follows:
	\begin{itemize}[nosep]
		\item \textbf{Custom Operator:} Since the main focus of the test is HRI, no custom operator can be chosen.
		\item \textbf{Alternative HRI:} Using an alternative HRI to understand a guest causes a score reduction \textcolor{red}{per information (name, drink or interest)}.
		\item \textbf{Recognizing People:} If the robot has to ask for help to identify people, score is reduced. 
		\item \textcolor{red}{\textbf{Non Essential Questions:} If the robot asks non essential questions to help understand or confirm information, score is reduced per question. 
		Questions such as "Did you say your name is James?", "Is your favorite drink milk?" or "Is your interest dancing?" are considered non essential questions. 
		However, asking a guest to repeat an answer because the robot could not hear is not considered a non essential question.}
	\end{itemize}
\end{enumerate}


\subsection*{Instructions}

\subsubsection*{To Referee}

The referees need to:
\begin{itemize}
	\item Assign name, drink and one interest to three volunteers.
	\item Arrange and rearrange people in the living room.
	\item Change the selection of drinks in the beverage area.
	\item Open the entrance door upon request from the robot.
\end{itemize}

\subsubsection*{To OC}


During setup day:
\begin{itemize}
	\item Announce the location of the beverage area.
\end{itemize}


At least two hours before test:
\begin{itemize}
	\item Announce the starting position.
	\item Announce host's name, favorite drink and interest.
	\item Recruit five volunteers: one as the host, two as arriving guests and two as passive guests.

\end{itemize}

% \newpage
\subsection*{Score sheet}
\input{scoresheets/Receptionist.tex}