\subsection{Serve Breakfast}
\label{test:serve-breakfast}
The robot has to set a table for breakfast for one person and prepare cereal for them.\\

\noindent \textbf{Main Goal:} Place breakfast items on a table (bowl, spoon, cereal box, and milk carton) and prepare cereal.\\

\noindent \textbf{Optional Goals:}
\begin{enumerate}[nosep]
	\item Pour milk into the bowl
	\item Place the spoon next to the bowl
\end{enumerate}

\subsubsection*{Focus}
\emph{Object perception}, \emph{manipulation}, and \emph{task planning}.

\subsubsection*{Setup}
\begin{itemize}[nosep]
	\item \textbf{Locations:}
		\begin{itemize}
			\item \textbf{Start location:} Before the test, the robot waits outside the \Arena{} and navigates to the kitchen when the door is open.
			\item \textbf{Test location:} The test itself takes place in the kitchen.
		\end{itemize}
		\item \textbf{People:}
			\begin{itemize}
				\item No people are involved in the test, unless the robot requires human assistance.
			\end{itemize}
	\item \textbf{Furniture:}
		\begin{itemize}
			\item \textbf{Table:} The robot serves breakfast on any table or flat surface in the kitchen (the team is free to choose this location).
			\item \textbf{Chairs:} Chairs may be placed around the kitchen table and won't be removed.
			\item \textbf{Doors:} The robot does not need to open any doors for finding the breakfast items.
		\end{itemize}
	\item \textbf{Objects:}
		\begin{itemize}
			\item All objects used in the test are in their predefined locations when the test starts.
		\end{itemize}
\end{itemize}

\subsubsection*{Procedure}
\begin{enumerate}[nosep]
	\item \textbf{Table selection:} Half an hour before the test starts, the team informs the referees about the surface that will be used as a table.
	\item \textbf{Test start:} The robot moves to the kitchen when the arena door is open.
	\item \textbf{Serving breakfast:} To serve breakfast, the robot has to place breakfast items on a table (bowl, spoon, cereal box, and milk carton).
	\item \textbf{Pouring cereal:} After placing the breakfast items on the table, the robot should pour cereal into the bowl.
	\item \textbf{Optional goals:}
		\begin{itemize}
			\item \textbf{Pouring milk:} After pouring cereal, the robot pours milk into the bowl in order to fully prepare the breakfast.
			\item \textbf{Placing the spoon next to the bowl:} In principle, the spoon can be placed anywhere on the table, but placing it next to the bowl is desired so that it is easily reachable by a person.
		\end{itemize}
\end{enumerate}

\subsubsection*{Additional Rules and Remarks}
\begin{enumerate}[nosep]
	\item \textbf{Safe placing:} Objects must be placed with care, namely the robot should place rather than throw or drop objects.
	\item \textbf{Deus ex Machina:} The scores are reduced if human assistance is received, in particular for:
	\begin{itemize}[nosep]
		\item pointing to an object or telling to the robot where an object is or where to place it
		\item handing an object over to the robot
		\item having a human place objects on the table
		\item having a human pour cereal into the bowl
	\end{itemize}
\end{enumerate}

\subsubsection*{OC Instructions}

During the \SetupDays:
\begin{itemize}
	\item Provide official cutlery and tableware for training.
\end{itemize}

\subsubsection*{Referee Instructions}

The referee needs to:
\begin{itemize}
	\item Remove all objects from the table.
	\item Place all objects in their default locations.
\end{itemize}

%\newpage
\subsubsection*{Score sheet}
%\input{scoresheets/ServeBreakfast.tex}
\input{skill_dict/score_sheets/serve_breakfast}

% Local Variables:
% TeX-master: "Rulebook"
% End:
