\section{Set the Table [Housekeeper]}
\label{test:set-the-table}
The robot has to set the table for dinner for one person.

% \subsection*{Focus}
% This test focuses on object perception, manipulation, and planning.

\noindent \textbf{Main Goal:} Neatly lay tableware and cutlery on the dining table (5 objects).

\noindent \textbf{Optional goals:}
\begin{enumerate}[nosep]
	\item Picking all utensils from the cupboard drawer
	\item Closing the cupboard drawer
	\item Laying a place mat first
\end{enumerate}

\subsection*{Focus}
\emph{Object recognition}, \emph{Object manipulation}.

%move pick utensils from drawer to bonus
% remove one of the items from pick ups
% add open cupboard to deus ex machina
%

\subsection*{Setup}
\begin{itemize}[nosep]
	\item \textbf{Locations:} This test takes place in the \Arena{}, in a room with a table and a cupboard.
	\item \textbf{Furniture:}
		\begin{itemize}
		 \item Chairs may be placed around the table and will not be removed.
		 \item The cupboard doors and drawers are initially closed.
		\end{itemize}
	\item \textbf{Objects}: 
	\begin{itemize}
		 \item 	The objects used in this test can be found in the cupboard, not in their predefined locations.
		 \item The following objects will be available in the cupboard:
		 \begin{itemize}
			\item\textit{Silverware}: Any two different objects (fork, knife, or spoon).
			\item\textit{Tableware}: A dish and any other object (bowl, cup, or mug).
			\item\textit{Napkin}: A cloth or paper napkin.
			\item\textit{Place mat}: A place mat will be at the bottom of all the object in the cupboard.
		 \end{itemize}
		 
		\end{itemize}
\end{itemize}

% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Procedure
% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Procedure}
\begin{enumerate}[nosep]

	\item \textbf{Open cupboard door:} The robot goes to the cupboard and opens the door.
	\item \textbf{Table setup:} The robot picks up five objects from the cupboard, and sets them on the table according to the following placement: 
		\begin{itemize}[nosep]
		 \item Knife and spoon must be placed to the right of the plate.
		 \item The mug or cup must be placed in front of the cutlery.
		 \item Fork and napkin must be placed to the left of the plate.
		 \item The bowl must be stacked on top of the plate.
		\end{itemize}

\end{enumerate}



\subsection*{Additional rules and remarks}
\begin{enumerate}[nosep]
	\item \textbf{Safe placing:} Objects must be placed with care. It must be clear that the robot is trying to place the object, not throwing or dropping it.

	\item \textbf{Deus ex Machina:} Score reductions are applied for requesting the following forms of human assistance:
	\begin{itemize}[nosep]
		\item \textbf{Handover:} Handing over an object.
		
		\item \textbf{Showing objects:} Pointing, or telling to the robot where an object is or where to place it.

	\end{itemize}

	\item \textbf{Cupboard drawers:} If a drawer is available near the cupboard, the team can decide to start the task with the cutlery in the drawer. The team can choose between having the robot open the cupboard door or the drawer, with the referee opening the other one.

\end{enumerate}

\subsection*{Referee instructions}

The referee needs to
\begin{itemize}
	\item Remove all objects from the table
	\item Place objects in their starting position (in the drawer or in the cupboard)
	\item Close the door or drawer, depending on which one the robot is going to attempt to open.
\end{itemize}

\subsection*{OC instructions}
During \SetupDays
\begin{itemize}
	\item Provide official cutlery and tableware for training.
\end{itemize}

% \newpage
\subsection*{Score sheet}
\input{scoresheets/SetTable.tex}

% Local Variables:
% TeX-master: "Rulebook"
% End:

