\section{Stickler for the Rules [Party Host]}
\label{test:stickler-for-the-rules}

\subsection*{Description}
The robot needs to make sure the house rules are followed.

\textbf{Main goal:}
Identify party guests breaking the house rules, politely clarify to the guest what to do and confirm that the guest is following the rule.

\textbf{Optional goal:}
Politely clarify to the guest what rule is being broken.


\subsection*{Focus}
This task focuses on
\textit{Object perception},
\textit{Human perception},
\textit{Action recognition} and
\textit{Verbal interaction}.

\subsection*{Setup}
\begin{itemize}[nosep]	
	\item \textbf{Locations:} 
	\begin{itemize}
		\item This task takes place inside the \Arena{}.
		\item The robot starts at a predefined location in the living room.
		\item There are a forbidden room in the house.
	\end{itemize}	 
	\item \textbf{People:} 
	\begin{itemize}
		\item There are at least five party guests inside the \Arena{}.
		\item Four of the guests are breaking rules.
		\item Guests may not follow the robot's instructions.
	\end{itemize}
	\item \textbf{Furniture:} All furniture are in their predefined locations.
	\item \textbf{Objects:} All objects are in their predefined locations.
\end{itemize}

\subsection*{Procedure}
	\begin{enumerate}[nosep]
		\item The referee requests the team to move the robot to the start location.
		\item The referee gives the start signal and starts the timer.
		\item The team leaves the area after the start signal.		
		\item A TC member follows the robot ready to press the emergency stop button.
		\item The robot Identify party guests breaking the house rules.
		\item The robot politely clarify to the guest what to do. 
		\item The robot confirm that the guest is following the rule.	
		\item \textbf{Optionally} and Politely, the robot clarify to the guest what rule is being broken.
	\end{enumerate}


\subsection*{Additional rules and remarks}
\begin{itemize}[nosep]
	\item \textbf{House Rules:}
	\begin{enumerate}[nosep]
		\item \textit{No shoes inside the house.}\\
		\textbf{Policy:} All guests have to take off their shoes at the entrance.\\
		\textbf{Action:} Take the guests to the entrance and verify they takes off the shoes.
	
		\item \textit{Forbidden room}\\
		\textbf{Policy:} No guests are allowed in the \emph{Forbidden Room}. \\
		\textbf{Action:} Take the offenders with other party guests and verify they doesn't enter back.
	
		\item \textit{No littering}\\
		\textbf{Policy:} Guests are not allowed to leave garbage on the floor.
		\textbf{Action:} Make the (closest) offender to pick up the garbage and throw it into the bin.
	
		\item \textit{Compulsory hydration}\\
		\textbf{Policy:} All guests must have a drink in hand at all times.\\
		\textbf{Action:} Take the guests to the kitchen/bar and make sure they grabs a drink.
	\end{enumerate}
\end{itemize}

\subsection*{Instructions:}
\subsubsection*{To Referee}

The referee needs to:
\begin{itemize}
	\item Instruct party guests on which rules to break.
	\item Assign each party guest a drink.
\end{itemize}

\subsubsection*{To OC}
The OC needs to:
\begin{itemize}
	\item \textbf{2 hours before the test:} Select and announce the robot start location.
	\item \textbf{2 hours before the test:} Select and announce which room is forbidden.
\end{itemize}

% \newpage
\subsection*{Score sheet}
\input{scoresheets/SticklerForRules.tex}

% Local Variables:
% TeX-master: "Rulebook"
% End:

