\section{Take Out the Garbage [Housekeeper]}
\label{test:take-out-the-garbage}
The robot picks up garbage from the floor and takes out the trash bags from the two bins in the apartment.

% \subsection*{Focus}
% This test focuses on object perception, manipulation, and planning.

\subsection*{Main Goal}
The area near the garbage bins is free of garbage, all garbage bins in the apartment are emptied and the garbage has been moved to a specified collection zone.


\noindent\textbf{Reward:} 500pts (150pts per bag, 100pts per item)

\subsection*{Bonus rewards}
\begin{enumerate}[nosep]
	\item Transporting both bags at once. (300pts)
\end{enumerate}

\subsection*{Setup}
\begin{itemize}[nosep]
	\item \textbf{Location:} This test takes place inside the arena.
	\item \textbf{Bins:} There are two small trash bins in different rooms of the apartment. They are roughly cylindrical and open at the top, though they are covered with a lid by default. The space above the bin will be free of obstructions. The bin may be placed against a wall. Bin locations are part of the communicated arena setup.
	\item \textbf{Objects:} Two unknown objects placed on the floor within view of the bins.
	\item \textbf{Bags:} Each bin contains a tied garbage bag with some light contents. The color of the bag is different from the color of the bin.
	\item \textbf{Collection Zones:} The collection zone is a designated area near the entrance.
\end{itemize}


\subsection*{Additional rules and remarks}
\begin{enumerate}[nosep]
	\item \textbf{Deus ex Machina:} The following reductions apply :
	\begin{itemize}
	    \item Removing the lid for the robot results in a score reduction of 75pts per lid.
		\item Handing a bag to the robot results in a score reduction of 75pts per bag.
		\item Handing an item to the robot results in a reduction of 75pts per item.
	\end{itemize}
	\item \textbf{Bag placement:} Placing a bag outside the collection zone results in a score reduction of 100pts per bag.
	\item \textbf{Manipulation:}  Tipping over a bin or tearing the bag results in a score reduction of 50pts per bag.

\end{enumerate}

\subsection*{Referee instructions}

The referee needs to
\begin{itemize}
	\item Place sealed bags with some light contents in the bins
	\item Ask team leader whether bins should be closed.
	\item Make sure collection zone is clear.
\end{itemize}

\subsection*{OC instructions}
During Setup days:
\begin{itemize}
	\item Provide official bins and bags for training.
\end{itemize}

2 hours before the test:
\begin{itemize}
	\item Announce the collection zones.
\end{itemize}

\subsection*{Score sheet}
\input{scoresheets/TakeOutGarbage.tex}

% Local Variables:
% TeX-master: "Rulebook"
% End:

