\section{Tidy Up}
\label{test:tidy-up}
 Inside a room in the arena are objects that don't belong there. The robot has to tidy up by bringing them back and throwing any unknown objects into the garbage.

\noindent \textbf{Focus:} \SysI, \NAV, \CV, \OR, \MAN.

\subsection*{Main Goal}
Find 5 misplaced objects in a room and bring them to their predefined locations.

\noindent\textbf{Reward:} 500pts (100pts per object).

\subsection*{Bonus Rewards}
\begin{enumerate}[nosep]
	\item Taking out the garbage (100pts).
	\item Moving a \emph{tiny} object (200pts).
	\item Moving a \emph{heavy} object (200pts).
\end{enumerate}


\subsection*{Setup and Procedure}
\begin{itemize}[nosep]
	\item \textbf{Location:} A random room in the arena.
	\item \textbf{Instruction:} Nearby the entrance, an operator tells the robot which room to clean.
	\item \textbf{Objects:} There are 5 misplaced objects at random locations in the room. Objects can be anywhere, including the floor, seats, and on furniture.
	All objects are clearly visible (i.e.~no occlusions) and can be:
	\begin{itemize}[nosep]
		\item\KnownObjects{}: Regular, alike, and standard objects.
		\item\UnknownObjects{}: Garbage lying around (2--3 objects).
	\end{itemize}
	\item \textbf{Heavy and Tiny Objects:} Objects used in this test are lightweight and average-sized.
	However, the team leader can request a tiny and a heavy object to be used and score additional points for moving them.
	\item \textbf{Bin:} There is an already tied trash bag inside the bin which the robot can bring to a predefined collection zone to score additional points. The unknown objects must be placed or dropped inside the, either emptied or still full, bin.
\end{itemize}

\subsection*{Additional Rules and Remarks}
\begin{enumerate}[nosep]
	\item \textbf{Partial Scoring:} The main task allows partial (per object) scoring.
	
	\item \textbf{Deus ex Machina:} Score reduction for requesting human assistance is applied per object as follows:
	\begin{itemize}[nosep]
		\item \textbf{Request Object Locations by Speech:} Telling the robot where an object can be found or should be placed causes a reduction of 30\% in scoring for that particular object.
		
		\item \textbf{Request Object Locations by Gesture:} Pointing at an object to be picked up or where to place an object causes a reduction of 40\% in scoring for that particular object.
		
		\item \textbf{Request Object Locations by Guiding:} Guiding the robot nearby the location where an object can be found or should be placed causes a reduction of 20\% in scoring for that particular object.
		
		\item \textbf{Request Object Interaction:} Having a human pick up or place an object causes a reduction of 60\% in scoring for that particular object.
	\end{itemize}
\end{enumerate}

\subsection*{Referee Instructions}
The referee needs to
\begin{itemize}
	\item Place the objects in the room.
	\item Recover disposed objects from the bin and place the trash bag inside.
	\item Ask teams whether they want a heavy or tiny object.
\end{itemize}

\subsection*{OC Instructions}
2 hours before the test:
\begin{itemize}
	\item Announce the location of the garbage collection zone.
\end{itemize}

\subsection*{Score Sheet}
\input{scoresheets/TidyUp.tex}
