\section{What is That?}
\label{test:what-is-that}
A guest asks the robot to identify objects in the household.

\noindent \textbf{Focus:} \SysI{}, \HRI{}, \GestRec{}, \CV{}, \OR{}.


\subsection*{Main Goal}
The robot names 5 objects, the operator is pointing at.

\noindent\textbf{Reward:} 1000pts (200pts per object)


\subsection*{Bonus Rewards}
\begin{enumerate}[nosep]
	\item The robot understands two different non-verbal commands, e.g., nodding, gesturing for the robot to follow (250pts)
	\item The robot names one feature that is unique to the object in its group (100pts, each)
\end{enumerate}


\subsection*{Setup and Procedure}
\begin{enumerate}[nosep]
	\item \textbf{Location:} This test takes place inside the \Arena{}.

	\item \textbf{Groups of Objects:} There are five groups of 2--5 \KnownObjects{} randomly placed on the floor.
	
	\item \textbf{Guest:} The guest is one of the referees. They will step in front of the robot after it enters the \Arena{} and guide them to a group of objects where they point at one.

	\item \textbf{Naming:} The robot needs to tell the guest the official name of the object.

	\item \textbf{Skipping Groups:} The robot can decide to pass on an object. The guest will move on to the next group. They robot cannot request to go back at a later time.
	
	\item \textbf{Non-Verbal Commands:} The team leader can tell the referee that the robot can recognize non-verbal commands. The team is not allowed to instruct the guest. Interaction must be guided by the robot.
\end{enumerate}


\subsection*{Additional Rules and Remarks}
\begin{enumerate}[nosep]
	\item \textbf{Partial Scoring:} The main task allows partial (per object) scoring.
	
	\item \textbf{Deus ex Machina:} Score reduction applies per object as follows:
	\begin{itemize}[nosep]
		\item \textbf{Asking Yes or No Questions:} Asking yes or no questions about the object (e.g. Is the object yellow?), reduces the score by 50pts.
		\item \textbf{Asking Attribute Questions:} Asking questions about attributes of the object (e.g. What color is the object?), reduces the score by 100pts.
		\item \textbf{Interacting with Objects:} Asking the operator to pick up the object or move it closer reduces the score by 150pts.
	\end{itemize}
\end{enumerate}

\newpage

\subsection*{Referee Instructions}

The referee needs to
\begin{itemize}[nosep]
	\item Place the groups of objects.
	\item Chose which objects to point at.
\end{itemize}

\subsection*{Score Sheet}
\input{scoresheets/HandMeThat.tex}

% Local Variables:
% TeX-master: "Rulebook"
% End:
