\section{Where is This? [Party Host]}
\label{test:where-is-this}
The robot has to explain and show people where they can find places in the \Arena{} (for example, \emph{Where is the TV?}). The robot has to tell the operator how to get to the desired location and then monitor that the operator reaches the intended location.

\noindent \textbf{Main Goal:} Give accurate directions and guide at least 3 people.

\noindent \textbf{Optional goals:}
\begin{enumerate}[nosep]
	\item Lead a non-expert operator to the destination correctly.
	\item Provide new instructions based on the previous ones.
	\item Guide the operator in a \emph{natural} way (for instance, pointing at the described objects and looking at the operator when speaking with them).
\end{enumerate}

\subsection*{Focus}
\emph{Person Leading}, \emph{Social Navigation}, \emph{Human-Robot Interaction}.


\subsection*{Setup}
\begin{itemize}[nosep]
	\item \textbf{Locations:} 
	\begin{itemize}
	 \item All predefined locations inside the \Arena{} are valid destinations.
	 \item \textbf{Start Location}:  The robot starts outside the \Arena{}. 
	 \item \textbf{Information Point}: The robot waits for the operator at the \emph{Information Point}, which can be anywhere in the \Arena{}, and is known to the robot. 
	\end{itemize}
		\item \textbf{People:} three people will act as operators. Upon request from the team, non-expert people may be recruited.
\end{itemize}


\subsection*{Procedure}
\begin{enumerate}[nosep]

	\item \textbf{Robot enters:} When the door opens, the robot navigates to the \emph{Information Point}.
	\item \textbf{Operators:} When the robot is waiting for a person, the next operator goes to the \emph{Information Point}, and asks the robot to be led to a particular location. Out of the three runs, two will have the same operator, returning for new directions to a new destination.
	\item \textbf{Give instructions:} The robot gives instructions to the operator and then starts to follow them.
	\item \textbf{Tour guide:} As robot and operator navigate to the target location, the robot explains what parts of the arena they are going through.
	\item \textbf{Execution monitoring:} The robot monitors the operator to provide additional instructions or corrections as needed.
	\item \textbf{Return to \emph{Information Point}:} After guiding each operator, the robot must return to the \emph{Information Point}.

\end{enumerate}

\subsection*{Additional rules and remarks}
\begin{enumerate}[nosep]
	\item \textbf{Deus ex Machina:} scores are reduced if the robot requires assistance as follows:
	\begin{itemize}[nosep]
		\item \textbf{Bypassing speech recognition:} communicating with the robot through a graphical interface, or any other way.
		
		\item \textbf{Operator's assistance:} Helping the robot find the operator (for instance, through waving or shouting).
	\end{itemize}

	\item \textbf{Non-expert Operators:} Optionally, questions can be asked by a \emph{Non-expert Operator}, that is, a person from the audience with no background in robotics. \emph{Non-expert Operators} are allowed to rephrase commands given by the referees.
	\\\textbf{Remark:} Referees are not allowed to instruct non-expert operators on how to operate the robot. \textbf{Teams attempting to instruct or bias the operator will be disqualified}.

	\item \textbf{Operator fallback:} If the robot consistently fails to understand the non-expert operator (3 times or more), teams can default to a regular operator.
	
	\item \textbf{Data Recording:} Only when using non-expert operators, a team can get an additional scoring bonus by providing the recording and transcript of the issued commands.

\end{enumerate}

\subsection*{OC instructions}
2 hours before the test:
\begin{itemize}
	\item Generate two destinations per volunteer, such that the directions for the second one can be based on directions for the first one.
	\item Recruit at least 2 volunteers for the test
	\item Instruct volunteers where things are in the house
	\item Announce the location of the \emph{Information Point}.
\end{itemize}

\subsection*{Referee instructions}
The referee needs to
\begin{itemize}
	\item Assign destinations to each volunteer.
\end{itemize}

\subsection*{Score sheet}
\input{scoresheets/WhereIsThis.tex}
