\section{Clean up the table [DSPL \& OPL]}
The robot has to remove all dishes from a table (presumably after dinner), and clean it up.

\subsection{Focus}
This test focuses on HRI, semantic mapping, object perception and manipulation.

\subsection{Setup}
\begin{itemize}
	\item \textbf{Location:} This test takes place in the arena. A dining table is located close to the sink (or dishwasher).
	\item \textbf{Sink:} The sink (or dishwasher) is near the table, preferably located in the same room.
	\item \textbf{Table setting:} The table has several objects disposed in a typical setting for a meal for one person. These objects include tableware (e.g. place mats, napkins, dishes, glasses), silverware (e.g. forks, spoons, knives), and food leftovers.
	\item \textbf{Spot:} There is a spot on the table next to the table setting.
\end{itemize}

\subsection{Task}
	\begin{enumerate}
		\item \textbf{Entering the arena:} The robot enters the arena and navigates to the designated location.
		\item \textbf{Fetching command:} The operator requests the robot to clean up the table.
		\item \textbf{Clean the table:} The robot takes all the tableware and cutlery to the sink or dishwasher, as instructed (team's choice). Food leftovers are either disposed in the trash bin or taken to their predefined location (e.g. fridge).
		\item \textbf{Scrub spots and spills:} The robot detects spots and spills on the table and clean them up using the cleaning cloth or sponge it has retrieved previously.
		\item \textbf{Leave the arena:} The robot leaves the arena once it has finished cleaning.
	\end{enumerate}

\subsection{Additional rules and remarks}
\begin{enumerate}
	\item \textbf{Collisions:} Slightly touching the table is allowed, as well as slightly pushing some objects. However, driving over the objects or any other form of a major collision is not allowed, and the referees directly stop the robot (Section \refsec{rule:safetyfirst}).

	\item \textbf{Objects:} A total of 6 objects are used in this test following the distribution shown below:
	\begin{itemize}
		\item\textit{Silverware}: Any two objects.
		\item\textit{Tableware}: Any two objects, excluding silverware. At least one must be a dish or a bowl.
		\item\textit{Food leftovers}: Any two edible or drinkable objects, regardless its category. One shall be disposed and the other stored for later use.
	\end{itemize}
	All objects used in this test are taken from the list of standard objects (See \ref{rule:scenario_objects}). Tableware and silverware are considered to be known to the robot.

	\item \textbf{Spots and Spills:} The referees must place a spot (e.g. jam or chocolate syrup) or spill some liquid (e.g.milk) on the table before the test starts. The substance used to create the spot shall be clearly visible and contrasting with the table. When cleaning it, it must be clear the robot has detected the spot and is trying actively to clean it. The selection of the cleaning tool (sponge or cloth) is made by the team.\\
	\textbf{Remark:} When possible, no tablecloth will be used to ease cleaning. If removing the tablecloth is not possible, a dry spot will be used instead (e.g. breadcrumbs or coffee powder).

	\item \textbf{Sink and dishwasher:} Is up to the team to decide whether the robot will place the objects in the sink or in the dishwasher (when available). It is acceptable if the robot stacks the dishes next to the sink instead of placing them inside it.

	\item \textbf{Human-Robot Interaction:} The robot is allowed to
	\begin{enumerate*}[label={\alph*)}]
	\item indicate the location of the cloth or sponge,
	\item ask the human operator what to do with food leftovers,
	and
	\item request operator's help to find the spot (e.g. pointing at it).
	\end{enumerate*}
	This interaction is extensible to any kind of reasonable request from the robot when attempting to solve the task.

\end{enumerate}

\subsection{Data recording}
  Please record the following data (See \refsec{rule:datarecording}):
  \begin{itemize}
   \item Images of recognized objects
   \item List of moved items
  \end{itemize}

\subsection{Referee instructions}

The referee needs to
\begin{itemize}
	\item Place the table setting.
	\item Clean spots smudged by the previous robot.
	\item Place the new spot meant to be clean.
	\item Recover objects from the trash bin.
\end{itemize}

\subsection{OC instructions}
During Setup days:
\begin{itemize}
	\item Provide official cutlery and tableware for training.
\end{itemize}

2 hours before the test:
\begin{itemize}
	\item Announce the predefined location to take the command.
	\item Announce which food leftovers shall be stored.
	\item Announce which food leftovers shall be disposed.
\end{itemize}

\newpage
\subsection{Score sheet}
\input{scoresheets/CleanTheTable.tex}

% Local Variables:
% TeX-master: "Rulebook"
% End:
