\section{Speech Recognition \& Audio Detection Test}

This test is divided in two phases. First the robot must answer a set of questions to an operator at the first attempt without asking for confirmation. The operator is not allowed to move to the robot or shout to the robot.

For the second phase, the Operator will move behind the robot and ask a set of questions which the robot must answer. The robot is allowed to turn to the operator and ask it to repeat the question, and the operator will repeat the question only once before moving again behind the robot and proceed with the next question.

\subsection{Goal}
The robot must be able to properly recognize and answer to a specific set of questions without ask for confirmation. Also, the robot shall be able to react to a speaking operator which is not facing to it.

\subsection{Focus}

This test focuses on voice recognition and audio-source localization in a noisy environment, with moving sound sources\footnote{This test may also be held outside the arena}.

\subsection{Setup}
\begin{enumerate}
\item The apartment is in its normal state.
\item All doors of the apartment are open, except for the entry door. 
\end{enumerate}

\subsection{Task}

\begin{enumerate}
\item \textbf{Direct speech recognition: } The robot should move (or be moved) to a previously specified point inside the arena. 
  A TC member will ask 5 questions from the set of 50 predefined questions in front of the robot. 
  The robot should answer the question without asking confirmation.
  A question will only be asked once; there are no repetitions of a question. 
\begin{itemize}
\item The operator shall be standing still and facing to the robot.
\item The operator shall be between 0.75 and 1.0 meters away from the robot position.
\item The operator shall be between -60$^{\circ}$ and 60$^{\circ}$ from the robot's center (front range).
\end{itemize}
\item \textbf{Indirect speech recognition: } A TC member will ask another 5 question of the same set, but standing outside the front range of the robot at the same distance. 
  The robot can do one of two things (each providing different amount of points):
\begin{itemize}
\item The robot may turn its microphone towards the operator and ask for only one repetition of the question. 
  The robot should then answer without asking for confirmation.
\item The robot may directly answer the question without turning towards the operator and without asking for confirmation.
\end{itemize}
\end{enumerate}


\subsection{Additional rules and remarks}

\begin{itemize}
\item \textbf{Continue rule:} Continue rule (Section \refsec{rule:asrcontinue}) can not be used during this test.
\item \textbf{Question timeout:} If the robot does not answer within 10 seconds, the question is considered as \textit{missed}, and the TC member will proceed with the next question.
\item \textbf{Understanding the answer:} If the robot's answer is not understood by the operator, it is considered as \textit{incorrect}, and the TC member will proceed with the next question. It is thus advised that the robot provide answers such that it is clear that the robot understood the question. For example, if the question is ``What is the capital of Germany?'', instead of just answering ``Berlin'', it is advised that the robot answers something to the effect of ``The capital of Germany is Berlin''.
\item \textbf{Question repetition:} In the second phase, if the robot turns towards the operator to be asked once again, it should clearly state that it requires a repetition of the question once it finishes turning, so as to queue the operator to do so.
\end{itemize}

\subsection{Referee instructions}

The referee needs to
\begin{itemize}
\item Avoid shouting to the robot.
\item Avoid getting closer to the robot.
\item Speak to the robot loud and clear with plain standard English.
\item Avoid repeating questions for the same robot.
\end{itemize}

\subsection{OC instructions}

\textbf{1 day before the test}
\begin{itemize}
\item Provide the set of 50 predefined questions
\end{itemize}
\textbf{2 hours before the test}
\begin{itemize}
\item Announce the placement of the robots
\end{itemize}

\subsection{Score sheet}
\input{scoresheets/SpeechRecognition.tex}

% Local Variables:
% TeX-master: "Rulebook"
% End:
