\section{TidyUp}
The robot's owner has just finished breakfast and made a mess of it. 
The robot is tasked with cleaning the breakfast table, which has some breakfast items on it and some food clutter. 

\subsection{Goal}
The robot must move the items on the table to their designated storage location in a nearby closet. 
When the items are out the way, some food clutter is left: peanut butter, juice, jam, chocolate pasta, chocolate sprinkles, etc. 
The robot must clean this off the table. 

\subsection{Focus}
This test focuses on grasping, door opening and cleaning. 

\subsection{Setup}
The robot starts waiting inside the arena. 
The table is located close to a closet in which the items must be placed. 
The door of the closet is closed and the robot should open it before placing the items. 

\begin{enumerate}
\item \textbf{Location:} One of the tables in the appartment.
\item \textbf{Closet:} The items must be stored in the closet which is close to the table. 
\end{enumerate}

\subsection{Task}
\begin{enumerate}
\item \textbf{Command:} When the robot is waiting, it is given the command to clean a table. The robot must clean the table the operator wants.
\item \textbf{Storing items:} The robot must store each item on the table in the closet. 
  The robot must announce what sort of object it is storing. 
  In case the robot does recognize the object it must announce this as well. 
\item \textbf{Cleaning the table:} The robot must clean the remaining food off the table. It may use a brush, cloth, etc. 
\item \textbf{Move out of the arena:} Once the table is clean, the robot must leave the arena. 
\end{enumerate}

\subsection{Additional rules and remarks}
\begin{enumerate}
\item \textbf{Multiple robots:} In case there are multiple tables with closets in the arena, multiple robots may perform this task in parallel. 
\item \textbf{Startup:} The robot starts waiting inside the arena and is commanded to start by a referee. 
\item \textbf{Single try:} The robot must be able to start from the first attempt. 
`There is no restart for this test. If the robot is unable to start it must be removed immediately.
\item \textbf{Single try:} The objects may be standing up (longest dimension vertical) of be laying down (longest dimension horizontal). 
\item \textbf{Collisions:} Slightly touching the table or closet is allowed. 
  Driving over the objects or any other form of a major collision is not allowed, and the referees directly stop the robot (Section \refsec{rule:safetyfirst}).
\item \textbf{Object types:} Some obects will be part of the \textit{Standard Objects Set} while another object may be an unknown item.
\item \textbf{Unknown objects:} When the robot encounters an unknown object, it may describe the object to the operator. E.g. say ``This is something I don't know, but it is a large, orange box''.
\item \textbf{Cleaning tool:} In case the robot did not bring a cleaning tool (e.g. a brush, cloth,  ...) itself, 
  the team may request a tool of choice to be placed at a position of their choice. 
\end{enumerate}

\subsection{Data recording}
  Please record the following data (See \refsec{rule:datarecording}):
  \begin{itemize}
   \item Images
   \item Plans
  \end{itemize}

\subsection{Referee instructions}

The referee needs to
\begin{itemize}
\item Place the objects on the table
\item Put some food clutter on the table, between the objects. 
\item Close the door of the closet. 
\end{itemize}

\subsection{Score sheet}
\input{scoresheets/TidyUp.tex}