%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\penaltybig}{500~}
\newcommand{\penaltysmall}{250~}

\section{Special penalties and bonuses}\label{sec:special_awards}

\subsection{Penalty for not attending}\label{rule:not_attending}
\begin{enumerate}
	\item \textbf{Automatic schedule:} All teams are automatically scheduled for all tests.

	\item \textbf{Announcement:} If a team cannot participate in a test (for any reason), the team leader has to announce this to the \OC{} at least \timing{60 minutes} before the test slot begins.

	\item \textbf{Penalties:} A team that is not present at the start position when their scheduled test begins is not allowed to participate in the test.
	If the team has not announced its absence, it receives a penalty of \scoring{\notattendingpenalty{} points}.
\end{enumerate}

\subsection{Extraordinary penalties}\label{rule:extraordinary_penalties}
\begin{enumerate}
	\item \textbf{Penalty for cheating:} If a team member is found cheating or breaking Fair Play, the team will be automatically disqualified from the running test, and receives a penalty of \scoring{\penaltybig points}.
	The \TC{} may also disqualify the team for the entire competition.

	\item \textbf{Penalty for faking robots:} If a team starts a test, but it does not solve any of the partial tasks (and is obviously not trying to do so), a penalty of \scoring{\penaltysmall points} is imposed.
	The decision is made by the referees and the monitoring \TC{} member.

	\item \textbf{Extra penalty for collision:} In case of major, grossly negligent collisions the \TC{} may disqualify the team for a test (the team receives \scoring{0 points}), or for the entire competition.

	\item \textbf{Not showing up as referee or assistant:} If a team does not provide a referee or assistant who is present at the Arena on time, the team receives a penalty of \scoring{\penaltysmall points}.

\end{enumerate}

\subsection{Bonus for outstanding performance}\label{rule:outstanding_performance}
\begin{enumerate}
	\item For every regular test, the @Home \TC{} can decide to give an extra bonus for \iterm{outstanding performance} of up to 10\% of the maximum test score.

	\item This is to reward teams that do more than what is needed to solely score points in a test but show innovative and general approaches to enhance the scope of @Home.

	\item If a team believes it deserves this bonus, it should inform the \TC{} in advance and provide a brief explanation.

	\item The decision to grant the bonus and its extent is solely at the discretion of the \TC{}.
\end{enumerate}
