\section{Robots}\label{rule:robots}

\subsection{Number of Robots}\label{rule:robots_number}

\begin{enumerate}
	\item \textbf{Registration:} The maximum \term{number of robots} per team is \emph{two}. Note, that a different configuration of a robot (i.e. alternative gripper) counts as a second robot. A robot needs to pass \RobotInspection \ in both configurations.
	\item \textbf{Regular Tests:} Only one robot is allowed per test. Different robots can be used for different test runs.
\end{enumerate}

\subsection{Appearance and Safety}\label{rule:robot_appearance}

Robots competing in the RoboCup@Home League must comply with security specifications to ensure they do not pose any risk to people or property while operating.
\begin{enumerate}
	\item \textbf{Cover:} All internal hardware (electronics and cables) must be fully enclosed to ensure safety.
	\item \textbf{Appearance:} Robots should present a product-like, finished appearance rather than an early-stage prototype. While improvised coverings (e.g. a t-shirt) are not explicitly prohibited, they are strongly discouraged. %Visible duct tape is strictly prohibited.
	\item \textbf{Loose cables:} No loose cables should hang out of the robot.
	\item \textbf{Safety:} The robot must not have sharp edges or protruding parts that could harm people.
	\item \textbf{Annoyance:} The robot must not emit continuous loud noises or use blinding lights.
	\item \textbf{Marks:} The robot must not display any artificial marks or patterns.
	\item \textbf{Driving:} Obstacle avoidance is mandatory to ensure safe movement.
\end{enumerate}
The compliance with these rules will be verified during \RobotInspection{} (see \ref{sec:robot_inspection}).

Humanoid Robots (2026): Legged humanoid robots are introduced to RoboCup@Home for the first time in 2026. Due to safety considerations, teams are permitted to use a safety crane/hanger system during task execution. The crane may be operated by one designated team member. This operator may only handle the crane and must not make physical contact with the robot at any time. Any direct contact between the operator and the robot will result in the immediate termination of the task.
Any major collision between the robot and the crane structure will be treated as a robot collision and will result in task termination. The crane operator is responsible for maneuvering the crane safely around the robot and the environment. Minor contact between the crane and door frames is permitted while passing through doorways. Outside of this exception, any major collision between the crane and the environment will be considered a collision and result in task termination.
Teams are responsible for ensuring that both the robot and the crane system can safely navigate all competition spaces, including passing through doorways and other environmental constraints.

\subsubsection{Size and Weight}\label{rule:robots_size}

\begin{enumerate}
	\item \textbf{Dimensions:} The robot must fit within the dimensions of an average door, which are typically \SI{200}{\centi\meter} by \SI{70}{\centi\meter} in most countries.
	The \TC{} allows the qualification and registration of larger robots, but they cannot guarantee that these robots can actually enter the \Arena{} due to local restrictions.
	If in doubt, please contact the \LOC{}.
	\item \textbf{Weight:} While there are no specific weight restrictions, the robot's total weight and the pressure it exerts on the floor must not exceed local regulations for the construction of offices and/or buildings in the country where the competition is held.
	\item \textbf{Transportation:} Team members are responsible for quickly removing the robot from the \Arena{}.
	The robot must be transportable by the team members in a way that is both quick and easy.
\end{enumerate}

\subsubsection{Emergency Stop Button}\label{rule:robots_emergency_button}

\begin{enumerate}
	\item \textbf{Accessibility and visibility:} Each robot must have an easily accessible and visible \EmergencyStop{} button.
	\item \textbf{Color:} \EmergencyStop{} buttons must be colored red and must be the only red buttons on the robot.
	The \TC{} may ask the team to tape over or remove any other red buttons present on the robot.
	\item \textbf{Robot behavior:} When an \EmergencyStop{} button is pressed, the robot and all its parts must stop moving immediately.
\end{enumerate}

\subsubsection{Start Button}\label{rule:start_button}

\begin{enumerate}
	\item \textbf{Requirements:} As explained in~\refsec{rule:start_signal}, teams that cannot perform the default start signal (opening the door) must provide a \StartButton{} that can be used to start tests.
	Teams must inform the TC in advance of any test that involves a start signal, including the \RobotInspection{}.
	\item \textbf{Definition:} The \StartButton{} can be any \enquote{one-button procedure} that is easy for a referee to execute, such as releasing the \EmergencyStop{}, pressing a green button, or using a software button in a graphical user interface.
\end{enumerate}

\noindent\textbf{Note:} All robot requirements will be tested during the \RobotInspection{} (see~\ref{sec:robot_inspection}).




