\section{Clean Up [Housekeeper]}
\label{test:clean-up}

\subsection*{Description}
	The robot has to clean up an \Arena{} room with some misplaced objects, placing unknown objects in a garbage bin.

\textbf{Main goal:}
	Find six misplaced objects in a room and bring them to their predefined locations.

\textbf{Optional goal:}
	Manipulate heavy and tiny objects.

\subsection*{Focus}
	This task focuses on 
	\textit{Task Planning},
	\textit{Object Perception} and
	\textit{Object Manipulation}.

\subsection*{Setup}
\begin{itemize}[nosep]	
	\item \textbf{Locations:} 
		\begin{itemize}
			\item This task takes place in a random room in the \Arena{}.
			\item The robot starts inside the \Arena{} at a predefined location near the entrance door.
		\end{itemize}
	\item \textbf{People:} Near the entrance, an operator tells the robot which room to clean.
	\item \textbf{Furniture:} All furniture are in their predefined locations.
	\item \textbf{Objects:} 
		\begin{itemize}
			\item There are 6--10 misplaced objects at random locations in the room.
			\item Objects can be anywhere in the room, including the floor, seats, and on top of furniture.
			\item All objects are clearly visible (i.e., no occlusions).
			\item Objects can be regular and alike (see \refsec{rule:scenario_objects}) or garbage lying around at grasping distance.
			\item Objects used in this test are lightweight and average-sized (see~\refsec{rule:scenario_objects}). The team leader can, however, request a tiny and a heavy object to be used in order to score additional points for picking them.
			\item Objects must be placed inside the bin, not thrown or dropped.
		\end{itemize}
\end{itemize}

\subsection*{Procedure}

\begin{enumerate}
	\item The referee requests the team to move the robot to the start location.
	\item The referee gives the start signal and starts the timer.
	\item The team leaves the area after the start signal.
	\item A TC member follows the robot ready to press the emergency stop button.
	\item The robot finds six misplaced objects in a room and brings them to their predefined locations.
	\item \textbf{Optionally}, the robot can manipulate heavy and tiny objects.
\end{enumerate}

\subsection*{Additional rules and remarks}
	No additional rules and remarks.

\subsection*{Instructions:}

\subsubsection*{To Referee}

The referee needs to:
\begin{itemize}
	\item Place objects in the room.
	\item Recover disposed objects from the bin.
	\item Ask teams whether they want a heavy or a tiny object to be 
\end{itemize}

\subsubsection*{To OC}
The OC needs to:
\begin{itemize}[nosep]
	\item \textbf{2 hours before the test}: Announce the starting location of the robot.
\end{itemize}

\subsection*{Score Sheet}
\input{scoresheets/old_score_sheets/CleanUp.tex}
