%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{External computing}\label{rule:robot_external_computing}
Robots are allowed to use some form of external computing, for example in the form of so-called \quotes{Cloud services} and/or \quotes{Internet API's} etc. 
\begin{enumerate}
	\item \textbf{Definition:} Computing resources that are not physical part of the robot are \iterm{external computing resources}. 
	\item \textbf{Inspection:} In general, external computers are not allowed unless explained to and allowed by the \iaterm{Technical Committee}{TC}.
	  A team must announce to the TC at least 1 month in advance the external computing resources they want to use, for what purpose and how to reach the resources (e.g. specify the URL or IP address and port). Inspected software must meet the following \textbf{requirements:}
	  \begin{itemize}
	  	\item The software must be open source (BSD/GPL/etc), or
        \item Detailed information about the propietary product must be provided (e.g. vendor, patent number, licencing, pricing, etc.), as well as publishing the interface for scientific use.
	  \end{itemize}
	All relevant information must be specified in the team description paper.
	\item \textbf{Connection:} The robot may connect to \iterm{external computing resources} via a network connection, e.g. the Internet. 
	  The competition organisation cannot make any guarantees concerning availability, connectivity and performance of the connection. 
	  The robot should still be functional (albeit limited perhaps) if the \iterm{external computing resources} cannot be used for some reason.
	  This is the team's responsibility. 
	\item \textbf{Autonomy:} The robot has to maintain full autonomy when using \iterm{external computing resources}, 
	  meaning there may not be a human giving the robot any kind of instructions via \iterm{external computing resources}.
	  It is up to the team to prove to the \iaterm{Technical Committee}{TC} that there was no cheating introduced via the \iterm{external computing resources}. 
	  For example, the use of Amazon Mechanical Turk to classify and recognize objects during a competition will be considered cheating, since effectively a human will do the classification.
	  Remote control or tele-operation is also considered cheating. 
	\item \textbf{Availability:} The resources must be publicly available, for use by robots of other teams, well before and after the competition.
	\item \textbf{Recognition:} In case the resources are not developed by the team itself, the creators must be properly credited in the Team Description Paper (See \refsec{rule:website_tdp}).
	\item \textbf{Limit:} A robot is limited to use up to 5 \iterm{external computing resources}. 
\end{enumerate}

\textbf{Remark:} Teams are allowed to use their own software in the external computing devices (not only cloud services). This software must be publicly available to other teams for scientific purposes (evaluation, test, and benchmarking), as well as for TC for inspection. Although open-sourcing the software is not mandatory, this practice is advised and encouraged by the league.

\subsection{External Computing Devices on site for SSPL (Hardware)}
\label{rule:robot_external_computing_devices_sspl}

\begin{itemize}
  \item \textbf{Location:} all external computing devices, approved by the \iaterm{Technical Committee}{TC}
  		(see~\ref{rule:robot_external_computing}), must be placed at a designated location close to the arena.
  		The location features a table (or otherwise suitable furnishing) and an ethernet switch (wired)
        that connects to the arena WIFI. In the remainder of this document, this location is called
  		\textbf{E}xternal \textbf{C}omputing\textbf{R}esource \textbf{A}rea (ECRA).
  \item \textbf{Procedure:} before a teams' test run, external comp. devices msut be setup in time.
  		Immediately after a teams' test slot, all equipment must be removed from the ECRA in order to give ensuing
        teams adequate space and time to setup their devices. No team should ever occupy the ECRA continuously.
  		As soon as the referee indicates the teams' test slot starts, team members are strictly forbidden to touch
        their external comp. devices until the current test run is over. Breaking this ``hands-off'' rule
        is penalized with 0 (zero) points for the corresponding test. Using external comp. devices during the test
        from any other location than the ECRA will be penalized with \textbf{at least 0 (zero) points for the test}.
  \item \textbf{Limitations:} external computing devices currently have no limitation concerning computation
  		power and form factor. However, in order to maintain enough space and a	clear arrangement (e.g. wrt
        inspectability for referees), stand-alone screens are \textbf{not allowed}. Mice and keyboards connected
        to external computing devices are allowed.
  \item \textbf{Recommendations:} show up in time and setup up your devices early enough. If your team is up last,
        do not setup first. Consider the ECRA a FIFO queue. There will be enough space at the ECRA to establish a
        buffer (of teams), so if you show up in time and everyone removes their equipment the transition will be smooth.
\end{itemize}

The referees, Technical Committee, and Organizing Committee members may run random checks anytime during the competition
to check if a team occupies the ECRA continuously or devices outside the ECRA are used to control the robot.


\subsection{Official Standard Laptop for DSPL}
\label{rule:osl_dspl}
% 
% Mandatory mounting bracket
% 
% In the Domestic Standard Platform League, teams are required to have the \iaterm{Official Standard Laptop}{OSL} connected to the Toyota HSR via Ethernet cable, safely located in the TOYOTA HSR \iterm{Mounting Bracket} provided by TOYOTA for this purpose.

% The robot must wear the \iterm{Mounting Bracket} with the OSL in all the tests during the competition and the OSL must be connected to the robot whether it's used or not. Since the use of the \iterm{Mounting Bracket} and the presence of the OSL is compulsory, teams missing this requirement will not be allowed to compete.

% 
% Optional mounting bracket
% 
In the Domestic Standard Platform League, teams may use the \iaterm{Official Standard Laptop}{OSL} connected to the Toyota HSR via Ethernet cable, safely located in the TOYOTA HSR \iterm{Mounting Bracket} provided by TOYOTA for this purpose.

\subsubsection{Technical Specifications}
The technical specifications for the Official Standard Laptop in the Domestic Standard Platform League are the following:


 \begin{itemize}
  \item \textbf{Brand and model:} DELL Alienware 15 or 17
  \item \textbf{CPU:} Core-i7 series
  \item \textbf{RAM:} 16GB or 32GB
  \item \textbf{GPU:} NVIDIA GeForce GTX 1070 or 1080
  \item \textbf{Storage:} Unrestricted.
\end{itemize}

No other brands or models will be accepted. There are no constrains regarding the software installed in the OSL but no additional hardware is allowed.

The referees, Technical Committee, and Organizing Committee members may run random checks anytime during the competition prior to the test to verify that the laptop in the TOYOTA HSR \iterm{Mounting Bracket} has no additional hardware plugged in, and matches the authorized specifications.

% Local Variables:
% TeX-master: "../Rulebook"
% End:
