\section{Robot Inspection}
\label{sec:robot_inspection}
Safety is the most important issue when interacting with humans and operating in the same physical workspace. Because of this, all participating robots are inspected before participating in RoboCup@Home. Every team needs to get their robot(s) inspected and approved so that they can participate in the competition.

\begin{enumerate}
	\item \textbf{Procedure:} The \RobotInspection{} is conducted like a regular test, namely it starts with opening of the arena door (see~\refsec{rule:start_signal}). One team after another (and one robot after another) has to enter the \Arena{} through a designated entrance door, move to the \textit{Inspection Point}, and leave the arena through the designated exit door. In between entering and leaving, the robot is inspected by the \TC.
	\item \textbf{Checked aspects:} During the \RobotInspection{}, each robot is checked for compliance with the competition rules (see~\refsec{rule:robots}), in particular:
	\begin{itemize}
		\item emergency button(s)
		\item collision avoidance (a TC member steps in front of the robot)
		\item voice of the robot (it must be loud and clear)
		\item custom containers (bowl, tray, etc.)
		\item external devices (including wireless network), if any
		\item Alternative human-robot interfaces (see~\refsec{rule:asrcontinue}).
		\item \textbi{Standard Platform robots}
		\begin{itemize}
			\item no modifications have been made
			\item specification of the \iaterm{Official Standard Laptop}{OSL} (if required)
		\end{itemize}
		\item \textbi{Open Platform robots}
		\begin{itemize}
			\item robot speed and dimension
			\item start button (if the team requires it)
			\item robot speaker system (plug for RF transmission)
			\item other safety issues (duct tape, hanging cables, sharp edges etc.)
		\end{itemize}
	\end{itemize}
	\item \textbf{Re-inspection:} If the robot is not approved in the inspection, it is the responsibility of the team to get the approval at a later point. Robots are not allowed to participate in any test before passing the \RobotInspection.
	\item \textbf{Time limit:} The robot inspection is interrupted after three minutes (per robot). When told so by the TC --- in case of time interrupt or failure --- the team has to move the robot out of the \Arena{} through the designated exit door.
	\item \textbf{Appearance Evaluation:} In addition to the inspection, the TC evaluates the appearance of the robots. Robots are expected to look nice (no duct tape, no cables hanging loose etc.). In case of objection, the TC may penalize the team with a penalty of maximum 50 points.
	\item \textbf{Accompanying team member:} Each robot is accompanied by only one team member (the team leader is advised).
	\item \textbf{OC instructions (at least two hours before the \RobotInspection):}
	\begin{itemize}
		\item Announce the entry and exit doors.
		\item Announce the location of the \textit{Inspection Point} in the \Arena{}.
		\item Specify and announce where and when the poster teaser and the poster presentation session take place.
	\end{itemize}
\end{enumerate}