\subsection{Robot Specifications for the Open Platform League }
Robots competing in the RoboCup@Home Open Platform League must comply with security specifications in order to avoid causing any harm while operating in human environments.

\subsubsection{Size and weight of robots}
\label{rule:robots_size}

\begin{enumerate}
	\item \textbf{Dimensions:} The dimensions of a robot should not exceed the limits of an average door, which is \SI{200}{\centi\meter} by \SI{70}{\centi\meter} in most countries.\\
	The TC may allow the qualification and registration of larger robots, but due to the international character of the competition it cannot be guaranteed that the robots can actually enter the arena. In case of doubt, contact the local organization.
	\item \textbf{Weight:} There is no specific weight restriction. However, the weight of the robot and the pressure it exerts on the floor should not exceed local regulations for the construction of buildings which are used for living and/or offices in the country where the competitions is being held.
	\item \textbf{Transportation:} Team members are responsible for quickly moving the robot out of the arena.	If the robot cannot move by itself (for any reason), the team members must be able to transport the robot away with an easy and fast procedure.
\end{enumerate}



\subsubsection{Emergency stop button}
\label{rule:robots_emergency_button}

\begin{enumerate}
	\item \textbf{Accessibility and visibility:} Every robot has to provide an easily accessible and visible \iterm{emergency stop} button.
	\item \textbf{Color:} It must be coloured red, and be the only red button on the robot.
	The TC may ask the team to tape over or remove any other red button present in the robot.
	\item \textbf{Robot behavior:} When the \iterm{emergency stop} button is pressed, the robot and all its parts must stop moving immediately.
	\item \textbf{Inspection:} The emergency stop button is tested during the \iterm{Robot Inspection} test (see~\refsec{sec:robot_inspection}).
\end{enumerate}




\subsubsection{Start button}
\label{rule:start_button}

\begin{enumerate}
	\item \textbf{Requirements:} As stated in~\refsec{rule:start_signal}, teams that aren't able to carry out the default start signal (opening the door) have to provide a \iterm{start button} that can be used to start tests.
	Teams need to announce this to the TC before every test that involves a start signal, including \iterm{Robot Inspection}.

	\item \textbf{Definition:} The start button can be any \enquote{one-button procedure} that can be easily executed by a referee (e.g. releasing of the \iterm{emergency button} (\refsec{rule:robots_emergency_button}), a green button, or a software button in a Graphical User Interface).
	\item \textbf{Inspection:} The start button is tested during the the \iterm{Robot Inspection} test (see~\refsec{sec:robot_inspection}).
\end{enumerate}




% \subsubsection{Audio output plug}
% \label{rule:roobt_audio_out}

% \begin{enumerate}
% 	\item \textbf{Mandatory plug:} Either the robot or some external device connected to it \emph{must} have a \iterm{speaker output plug}. It is used to connect the robot to the sound system so that the audience and the referees can hear and follow the robot's speech output.
% 	\item \textbf{Inspection:} The output plug needs to be presented to the TC during the \iterm{Robot Inspection} test (see~\refsec{sec:robot_inspection}).
% 	\item \textbf{Audio during tests:} Audio (and speech) output of the robot during a test have to be understood at least by the referees and the operators.
% 	\begin{compactitem}
% 		\item It is the responsibility of the teams to plug in the transmitter before a test, to check the sound system, and to hand over the transmitter to next team.
% 		\item Do not rely on the sound system! For fail-safe operation and interacting with operators make sure that the sound system is not needed, e.g., by having additional speakers directly on the robot.
% \end{compactitem}
% \end{enumerate}




\subsubsection{Appearance}
\label{rule:robots_appearance}
Open Platform Robots should have a neat appearance that resembles more a safe and finished product than an early stage prototype, paying special attention in completely cover the robot's internal hardware (electronics and cables) in an appealing way.
% However, teams must keep in mind that no artificial markers are allowed when personalizing the appearance or a robot. This includes, but is not limited to bar codes, QR codes, OpenCV markers, fluorescent and phosphorescent colors, and reflective stickers.
Although covering the robot's internal hardware with a T-Shirt is not forbidden (for now) it is strongly unadvised.