\subsection{Smart Home Devices}
\label{rule:smarthomedevices}

The Organizing and Technical Committees in coordination with the Local Organization will compile a list of \iterm{Smart~Home} official devices that will be available in the arena and can be used in some tests for additional score.

At any time, only the Smart~Home devices provided by the Local Organization and approved by the Technical Committee may be used during competition.

\subsubsection{Smart~Home devices list announcement}
The list if Smart~Home devices will be provided to teams as soon as it becomes available and has been granted by the Local Organization and approved by the Technical Committee. 

This list must be announced at least one month prior the competition. In case that this list does not become available for that date, Smart~Home devices may still be present at the arena for testing, but no additional score can be achieved for its use. This is to maintain fair conditions among all teams.

\subsubsection{Technical specifications}
The list of \iterm{Smart~Home} official devices will include as much technical information as possible. However, before it becomes available you may assume the following considerations:

\begin{enumerate}
	\item \textbf{Interface:} Most Smart~Home devices interface wireless, often via R/F transmitters. When possible, the OC will provide an official interface via the \iterm{arena network}.
	\item \textbf{Operating voltage:} The operating voltage used will be the standard for the place of the competition (e.g.120V/60Hz for North America and 220V/50Hz for Europe). Please note that devices designed for other voltages/frecuencies may burn when plugged to the outlet.
	\item \textbf{Type of devices:} Mostly Smart~Home switches will be used (set on/off, read can not be guaranteed). For high bandwidth devices such as microphones or video cameras, an official interface (such as a ROS topic or web service) will be provided via the \iterm{arena network}.
\end{enumerate}

\subsubsection{Availability \& Scoring}
All test has been designed to optionally allow the use of Smart~Home devices and even grant bonus scoring for using this option. However, robots must be able to continue operating normally when there are no Smart~Home devices available. Therefore, it is unacceptable that a robot gets stuck or in some sort of deadlock while trying to operate those devices.

As stated in \refsec{rule:scenario_wifi}, organizers cannot guarantee reliability and performance of wireless communication. Therefore, in case of malfunction or communication problems with the Smart~Home devices, or any other issue which may affect scoring, no claims will be accepted by the EC/TC/OC, nor test will be repeated. The decision on if a team given points for using \iterm{Smart~Home} devices, is conducted by the \iaterm{Technical Committee}{TC}, and it reserves the rights of discarding Smart~Home related scoring.


% Local Variables:
% TeX-master: "../Rulebook"
% End:
