%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%    author(s): RoboCupAtHome Technical Committee(s)
%%  description: Introduction - Infrastructure
%%
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Infrastructure}
\label{sec:infrastructure}
\subsection{RoboCup@Home Mailinglist}
The official \iterm{RoboCup@Home mailing list} can be reached at
\begin{center}
\href{mailto:robocup-athome@lists.robocup.org}{\texttt{robocup-athome@lists.robocup.org}}
\end{center}
You can register to the email list at:
\begin{center}
{\small\url{http://lists.robocup.org/cgi-bin/mailman/listinfo/robocup-athome}}
\end{center}

\subsection{RoboCup@Home Web Page}
The official \iterm{RoboCup@Home website} that also hosts this RuleBook can be found at:
\begin{center}
{\small\url{https://athome.robocup.org/}}
\end{center}

\subsection{RoboCup@Home Rulebook Repository}
The official \iterm{RoboCup@Home Rulebook Repository} is where rules are publicly discussed before applying changes to the rulebook.
The entire RoboCup@Home community is welcome and encouraged to actively participate in creating and discussing the rules. The repository can be reached at:
\begin{center}
{\small\url{https://github.com/RoboCupAtHome/RuleBook/}}
\end{center}

Although opening issues with inconsistencies, questions, clarifications, and suggestions is highly appreciated, the best way to contribute is by making pull requests with fixes and proposed changes.

\subsection{RoboCup@Home Telegram Group}
The official \iterm{RoboCup@Home Telegram Group} is and communication channel for the RoboCup@Home community where rules are discussed, announcements are made, and questions are answered.
However, beyond the technical aspects of the competition, the \textit{Telegram Group} is a meeting point to stay in contact with the community, foster knowledge exchange and strengthen relationships.
The \textit{Telegram Group} can be reached at
\begin{center}
{\small\url{https://t.me/RoboCupAtHome}}
\end{center}

\subsection{RoboCup@Home Wiki}
\label{sec:at_home_wiki}
The official \iterm{RoboCup@Home Wiki} is meant to be a central place to collect information on all topics related to the RoboCup@Home league. It was set up to simplify and unify the exchange of relevant information.
This includes but is certainly not limited to hardware, software, media, data, and alike.
The \textit{wiki} can be reached at:
\begin{center}
{\small\url{https://github.com/RoboCupAtHome/AtHomeCommunityWiki/wiki}}
\end{center}

