%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%    author(s): RoboCupAtHome Technical Committee(s)
%%  description: Introduction - Organization
%%
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Organization}

% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Executive Committee
%
% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Executive Committee --- ec@robocupathome.org}
\label{sec:ec}
The \iaterm{Executive Committee}{EC} consists of members of the board of trustees, and representatives of each activity area. The EC is responsible of the direction of the RoboCup@Home leagues, and has the last word in any decision taken. Is duty of the EC to instruct the new TC members when they join the committee, as well as instruct the OC Chair and supervise the decisions of both committees.

\subsubsection{Members representing the @Home league}
\begin{itemize}
  \item Kai Chen (University of Science and Technology of China, China)
  \item Dirk Holz (University of Bonn, Germany)
  \item Caleb Rascon (Universidad Nacional Autónoma de México, Mexico)
  \item Sven Wachsmuth (Bielefeld University, Germany)
\end{itemize}


% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Technical Committee
%
% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Technical Committee --- tc@robocupathome.org}
\label{sec:tc}
The \iaterm{Technical Committee}{TC} is responsible for the rules of each league. Its responsibilities include:

\begin{enumerate}
  \item During preparation time
  \begin{itemize}
    \item Write and buff the rules in the rulebook
    \item Design and write new tests (when applicable)
    \item Evaluate previous performance and update tests accordingly
  \end{itemize}
  \item During the competition
  \begin{itemize}
    \item Direct Q\&A sessions during Team Leader meetings
    \item Renounce to their teams and serves as referees (see \refsec{rule:referees})
    \item Take decisions about partial scores and penalties
  \end{itemize}
\end{enumerate}

The \iaterm{Technical Committee}{TC} is renewed every year, being its members elected by the participating teams. However, elected members still have to earn their place in the TC during the running year by actively contributing with the next-year's rulebook creation. The Executive Committee reserves to itself the legitimate right of replacing inactive TC members with more enthusiastic and participative people from the league who has been actively contributing during the year. It is advised that candidates work with the \iaterm{Organizing Committee}{OC} for one year before trying to join the Technical Committee.

The \iaterm{Technical Committee}{TC} does not have a Chair, but its actions are directed and supervised by the Executive Committee. All members of the EC are considered to be part also of the TC.

\subsubsection{Members of the RoboCup@Home Technical Committee for \YEAR}:
\begin{itemize}
  \item Justin Hart (University of Texas at Austin, USA)
  \item Raphael Memmesheimer (University of Koblenz-Landau, Germany)
  \item Sammy Pfeiffer (University of Technology Sydney, Australia)
\end{itemize}
The Technical Committee also includes the members of the Executive Committee.


% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Organizing Committee
%
% %% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Organizing Committee --- oc@robocupathome.org}
\label{sec:oc}
The \iaterm{Organizing Committee}{OC} is responsible for the organization of the competition. Its responsibilities include:

\begin{enumerate}
  \item During preparation time
  \begin{itemize}
    \item Review the Qualification Material and select teams for the competition (see \refsec{rule:participation})
  \end{itemize}
  \item During the competition
  \begin{itemize}
    \item Publish knowledge lists during setup days
    \item Schedule tests, and arena usage
    \item Organize volunteers, moderators, objects, etc.
    \item Take times during tests
    \item Guard the arena access during tests
    \item Organize queues during tests
    \item Retrieve signed scoresheets and capture scores
    \item Compute and publish scores
    \item Perform OC tasks stated in the rulebook
    \item Any other required logistic activities
  \end{itemize}
\end{enumerate}

The \iaterm{Organizing Committee}{OC} activities are directed by the \iterm{OC Chair}, and its members are self-elected by volunteering. Participants can join the Organizing Committee anytime just by committing to the OC Chair, however, only participants with at least two years of experience in RoboCup@Home can take par in the Qualification Procedure (see \refsec{rule:participation}).

\subsubsection{Members of the RoboCup@Home Organizing Committee for \YEAR}

\begin{itemize}
  \item[Chair] Mauricio Matamoros (University of Koblenz-Landau, Germany)
  \item Alexander William Moriarty (TBA, Bonn-Rhein-Sieg University; Germany)
  \item Fabrice Jumel (Université de Lyon; France)
  \item Francisco Javier Rodriguez Lera (University of Luxembourg, Luxembourg)
  \item Jesus Savage (Universidad Nacional Autónoma de México, Mexico)
  \item Jeffrey Too Chuan Tan (The University of Tokyo, Japan)
  \item Luz Martínez (Universidad de Chile, Chile)
\end{itemize}
